---
title: "Recoverability of market-wide fair insurance premiums under selection bias : R Code"
author: "Marie-Pier Côté, Olivier Côté, and Arthur Charpentier"
output: 
  html_document: 
    code_folding: show
    toc: yes
    toc_float: yes
    css: ../misc/style.css
    highlight: pygments
    theme: cosmo
editor_options: 
  chunk_output_type: console
---

# Libraries, user-defined functions and Python setup

```{r packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(latex2exp)
library(jsonlite)
library(reticulate)
library(lightgbm)
```

A few functions are required:

```{r source}
source('___functions.R')
```


Let's setup Python.

```{r setup, include=FALSE}
tryCatch({
  python_env_path <- get_python_env_path()
  use_python(python_env_path, required = TRUE)
  message("Python environment successfully set to: ", python_env_path)
}, error = function(e) {
  stop(e$message)
})
```

Choose the colors for the plots.

```{r setcolors}
colors_for_gg_D <- c("deeppink2", "#3B93C7") 
colors_for_gg_A <- c("#00C5CD", "#800080") 

colors_for_gg_market <- c("market" = "#B8C0CA",
                          "A=1" = colors_for_gg_A[2],
                          "A=0" = colors_for_gg_A[1]) 
colors_for_gg_premium <- c("best"="#000000",
                           "un"='#9966CC',
                           "aw"= '#F7798D',
                           'corr' = '#ffd332')

# blue '#96eaff' '#4ea0cf'
# vert '#a1ff91' '#60ff82'
# orange '#e5d14a'
```


# Simulation and exploratory plots

Now that we have functions, setup and simulate. 

The parameters for the base scenario.

```{r orig_param}
parms_original <- list('p' = 0.5, # P(D = 1), this the anchor point (root node)
                       
              'b_0' = 100, # beta0 for P(Y|X, D)
              'b_d' = 15, # betaD for P(Y|X, D)
              'b_x' = 3, # betaX for P(Y|X, D)
              'b_A' = 0, # betaA for P(Y|X, D) (moral hazard)
              'sd_Y' = sqrt(45), # sd for  P(Y|X, D) (gaussian)
                       
              'g_0' = 1, # gamma mean for P(X)
              'rho_xd' = 0.9, # rho for copula C(X, D)
              'sd_X' = 3, # sd for P(X|D) (gaussian)
                       
              'pA' = 0.5, # desired marginal dist for P(A = 1) (alpha0 deduced from there)
              'a_d' = -3, # alphaD for P(A|X, D)
              'a_x' = -0.5 # alphaX for P(A|X, D)
              )

n <- 1e5
```

The parameters for the six scenarios.

```{r scenario_param}
parms <- list('original' = parms_original,
              'neutral' = {tmp <- parms_original; tmp[['rho_xd']] <- 0; tmp},
              'noDtoA' = {tmp <- parms_original; tmp[['a_d']] <- 0; tmp},
              'noDtoY' = {tmp <- parms_original; tmp[['b_d']] <- 0; tmp},
              'nodiscr' = {tmp <- parms_original; tmp[['rho_xd']] <- 0; tmp[['b_d']] <- 0; tmp},
              'noselbias' = {tmp <- parms_original; tmp[['a_d']] <- 0; tmp[['a_x']] <- 0; tmp})


## (later used for ggplot2 titles)
long_labels_for_parms <- c("(a) Base scenario",
                      "(b) No link D to X",
                      "(c) No link D to A",
                      "(d) No link D to Y",
                      "(e) No discrimination",
                      "(f) No selection bias")
names(long_labels_for_parms) <- names(parms)
```

The simulations are saved into a separate folder. If the simulations already exist in the folder, we read them, otherwise we generate the data and save. For each scenario, we generate a training set, a validation set and a testing set.

```{r generate, include=FALSE}
set.seed(131929) 

## the simulation files
files_sims <- paste0('simuls/',
                     c('train', 'valid', 'test'),
                     '_scenarios.json')

## If the folder do not exist... 
if (!dir.exists('simuls')) {
  dir.create('simuls')
}

## We read the simulations, or we do them and save them (json for general data format and easy communication with Python)
if(file.exists(files_sims[1])){# load
  sims <- jsonlite::fromJSON(files_sims[1])
} else {# simulate and write
  set.seed(321) # original set.seed - no sel bias is weird for A=0
#  set.seed(2024225) # optional set.seed - other things are weird, so stick with the first choice.
  sims <- parms %>% lapply(function(parameters){
  simulate_ex_art(n = n, params = parameters)
  })
  sims %>% jsonlite::toJSON(., pretty = TRUE) %>% write(files_sims[1])
}

if(file.exists(files_sims[2])){ # load
  valid <- jsonlite::fromJSON(files_sims[2])
} else { # simulate and write
  set.seed(123)
  valid <- parms %>% lapply(function(parameters){
  simulate_ex_art(n = n/10, params = parameters)
})
  valid %>% jsonlite::toJSON(., pretty = TRUE) %>% write(files_sims[2])
}

if(file.exists(files_sims[3])){ # load
  test <- jsonlite::fromJSON(files_sims[3])
} else { # simulate and write
  set.seed(132)
  test <- parms %>% lapply(function(parameters){
  simulate_ex_art(n = n/10, params = parameters)
  })
  test %>% jsonlite::toJSON(., pretty = TRUE) %>% write(files_sims[3])
}

```

We first plot the response in terms of $D$ and the portfolio inclusion $A$ for each scenario.As expected, portfolio $A=1$ consists of lower risk individuals (except in scenario f) and individuals with $D=1$ are riskier.

```{r exploration1, fig.height=10, echo=FALSE}

# lapply(names(sims), function(pop_name) {
#   ggplot(sims[[pop_name]], aes(x=factor(D), y=Y, colour = factor(A)))+
#     geom_boxplot()+
#     scale_color_manual(values = colors_for_gg_A, name = "A")+
#     theme_minimal()+
#     labs(x="D",
#          title=long_labels_for_parms[pop_name])}) %>%
#   ggpubr::ggarrange(plotlist = .,
#                            nrow = 3, ncol=2,
#                            widths = 15, heights = 1,
#                            common.legend = T,
#                            legend = 'right')
  

(tosave_scenarios <- lapply(names(valid)[1:3], function(pop_name) {
  valid[[pop_name]] %>%
    sample_n(2.5e3) %>% 
    mutate(D = factor(D), A=factor(A))%>%
    ggplot( aes(x=X, y=Y, colour = D, shape=D))+
    geom_point(alpha=0.35)+
    facet_wrap(~A, 
               labeller = labeller(A=c("0" = "A=0", "1" = "A=1")))+
    scale_color_manual(values = colors_for_gg_D, name = "D")+
    theme_minimal()+
    ggtitle(long_labels_for_parms[pop_name])
    }) %>%
  ggpubr::ggarrange(plotlist = .,
                           nrow = 1, ncol=3,
                           widths = 12, heights = 1,
                           common.legend = T,
                           legend = 'right'))

ggsave(filename = "figs/graph_scenarios.pdf",
       plot = tosave_scenarios,
       height = 3,
       width = 9,
       units = "in",
       device = "pdf", dpi = 500)
```

# Plots of the theoretical expressions

We focus on the first three scenarios.


## Expectation of D given X and A

The expectation of $D$ given $X$ can be computed analytically.

```{r expDgivenX}
ExpDgivenX <- function(pop_name, x){
  g <- parms[[pop_name]]$g_0 
  rho_xd <- parms[[pop_name]]$rho_xd 
  sd <- parms[[pop_name]]$sd_X 
  1- pnorm((0-rho_xd*(x-g)/sd)/sqrt(1-rho_xd^2))
}

ExpDgivenXA <- function(pop_name, x, a){
 
  param <- parms[[pop_name]]
  
  rho_xd <- param$rho_xd 
  a_0 <- -1 * sum(param[['a_x']]*param[['g_0']] + param[['a_d']] * param[['p']])
 
  probAgivenXD1 <- (exp(a_0+param[['a_x']]*x+param[['a_d']]))^(a==1)/(1+exp(a_0+param[['a_x']]*x+param[['a_d']]))
  
  probAgivenXD0 <- (exp(a_0+param[['a_x']]*x))^(a==1)/(1+exp(a_0+param[['a_x']]*x))
    
  expDgivenX <- 1- pnorm((0-rho_xd*(x-param$g_0 )/param$sd_X)/sqrt(1-rho_xd^2))
  
  expDgivenXAnum <- probAgivenXD1*expDgivenX
  
  expDgivenXAnum/(expDgivenXAnum +probAgivenXD0*(1- expDgivenX))
}

par(mfrow=c(2,3))
for (j in names(parms)){
curve(ExpDgivenX(j, x), -10,10, ylab="E(D|X=x)", main=long_labels_for_parms[[j]], ylim=c(0,1))
curve(ExpDgivenXA(j, x, 1), add=TRUE,col=colors_for_gg_A[2], lty=2)
curve(ExpDgivenXA(j, x, 0), add=TRUE,col=colors_for_gg_A[1], lty=3)
}

```

Plot the Prob that D=1 given X and given X and A for the first three scenarios.

```{r plotExpDgivenXA, fig.width=12,fig.height=6, echo=FALSE}
short_grid <- expand.grid(x = parms_original$g_0 + 
                            parms_original$sd_X * 
                            qnorm(seq(0.001, 0.999, by = 0.01)),
                             d = 0:1)

(to_save_theo_expDgivenX <- names(parms)[1:3] %>% 
  lapply(function(pop_name){
    
    toplotDat <- short_grid %>% 
      mutate(market = sapply(1:nrow(short_grid), function(i){ 
        ExpDgivenX(pop_name,short_grid[i, 'x'])}),
        "A=1" = sapply(1:nrow(short_grid), function(i){
        ExpDgivenXA(pop_name,short_grid[i, 'x'], 1)}),
        "A=0" = sapply(1:nrow(short_grid), function(i){
        ExpDgivenXA(pop_name,short_grid[i, 'x'], 0)})
        ) %>% 
      reshape2::melt(measure.vars = c('market', 'A=0','A=1'))
    
    pop_id <- which(names(sims) == pop_name)
    
    # keep only axis for last plot
    if(which(pop_name == names(sims)) == 1){
      the_y_label <- latex2exp::TeX("$E(D|X=x, A)$")
      the_y_scale <- scale_y_continuous(breaks = seq(0, 1, by=0.5), limits=c(0,1))
      the_x_label <- latex2exp::TeX("$x$")
      } else { 
      the_y_label <- NULL
      the_y_scale <- scale_y_continuous(breaks = seq(0, 1, by=0.5), limits=c(0,1))
      the_x_label <- latex2exp::TeX("$x$")
    }
      
      
    toplotDat %>% ggplot(aes(x = x, y = value,
               col = variable, linetype = variable,
               linewidth=variable
               )) + 
      geom_line(alpha = 0.75) + 
  labs(x = the_x_label,
       y = the_y_label,
       title = latex2exp::TeX(long_labels_for_parms[pop_id])) + 
      scale_x_continuous(breaks = c(-3:3)*3 + 1)  + # see above
      the_y_scale +
  theme_classic()+
#  theme_minimal()+
  theme(plot.title = element_text(hjust=0.5))+
  scale_color_manual(values = colors_for_gg_market, name = "A") +
  scale_linetype_manual(values = c(1, 2,3), name = "A") +
  scale_linewidth_manual(values = c(1.5,1, 1.2), name = 'A') 
  }) %>% ggpubr::ggarrange(plotlist = .,
                           nrow = 1, ncol=3,
                           widths = 15, heights = 1,
                           common.legend = T,
                           legend = 'right'))



ggsave(filename = "figs/graph_theo_expDgivenXA.pdf",
       plot = to_save_theo_expDgivenX,
       height = 2.00,
       width = 8,
       units = "in",
       device = "pdf", dpi = 500)
```


Expectation of D given A for Table in article.

```{r}
# Two functions we need to integrate numerically to get the aware premium by subportfolio

funtointegrate1 <- function(x,a,param){
  
  rho_xd <- param$rho_xd 
 a_0 <- -1 * sum(param[['a_x']]*param[['g_0']] + param[['a_d']] * param[['p']])
 
  probAgivenXD1 <- (exp(a_0+param[['a_x']]*x+param[['a_d']]))^(a==1)/(1+exp(a_0+param[['a_x']]*x+param[['a_d']]))
  
  expDgivenX <- 1- pnorm((0-rho_xd*(x-param$g_0 )/param$sd_X)/sqrt(1-rho_xd^2))
  
  probAgivenXD1*expDgivenX*dnorm(x,param$g_0,param$sd_X)
}

funtointegrate2 <- function(x,a,param){
  rho_xd <- param$rho_xd 
 a_0 <- -1 * sum(param[['a_x']]*param[['g_0']] + param[['a_d']] * param[['p']])
 
  probAgivenXD0 <- (exp(a_0+param[['a_x']]*x))^(a==1)/(1+exp(a_0+param[['a_x']]*x))
  
  expDgivenX <- pnorm((0-rho_xd*(x-param$g_0 )/param$sd_X)/sqrt(1-rho_xd^2))
  
  probAgivenXD0*expDgivenX*dnorm(x,param$g_0,param$sd_X)
}


expDgivenA <- function(param, a=1){
    num <- integrate(funtointegrate1, lower=-100, upper=100, a=a,param=param)$value
    denom2 <- integrate(funtointegrate2, lower=-100, upper=100, a=a,param=param)$value
  num/(num+denom2)
}

(toprintExpDgivenA <- parms %>% lapply(FUN=expDgivenA))

round(unlist(toprintExpDgivenA),3)
```

Plot for graphical abstract, scenario (a) only.

```{r plotExpDgivenXAscA, fig.width=6,fig.height=6, echo=FALSE}

pop_name <- names(parms)[1]

    toplotDat <- short_grid %>% 
      mutate(market = sapply(1:nrow(short_grid), function(i){ 
        ExpDgivenX(pop_name,short_grid[i, 'x'])}),
        "A=1" = sapply(1:nrow(short_grid), function(i){
        ExpDgivenXA(pop_name,short_grid[i, 'x'], 1)}),
        "A=0" = sapply(1:nrow(short_grid), function(i){
        ExpDgivenXA(pop_name,short_grid[i, 'x'], 0)})
        ) %>% 
      reshape2::melt(measure.vars = c('market', 'A=0','A=1'))
    
      
(to_save_theo_expDgivenX_ScA <-  ggplot(toplotDat, 
                                       aes(x = x, y = value,
               col = variable, linetype = variable,
               linewidth=variable
               )) + 
      geom_line(alpha = 0.75) + 
  labs(x = latex2exp::TeX("$x$"),
       y = latex2exp::TeX("$E(D|X=x, A)$")) + 
      scale_x_continuous(breaks = c(-3:3)*3 + 1)  + # see above
      scale_y_continuous(breaks = seq(0, 1, by=0.5), limits=c(0,1)) +
  theme_classic()+
#  theme_minimal()+
  theme(panel.background=element_rect(fill="transparent"),
        plot.background = element_rect(fill='transparent', color=NA),
        legend.background = element_rect(fill='transparent'),
        legend.position=c(0.25,0.8))+
  scale_color_manual(values = colors_for_gg_market, name = "") +
  scale_linetype_manual(values = c(1, 2,3), name = "") +
  scale_linewidth_manual(values = c(1.5,1, 1.2), name = ''))
  

ggsave(filename = "figs/graph_theo_expDgivenXA_ScA.pdf",
       plot = to_save_theo_expDgivenX_ScA,
       height = 1.75,
       width = 2.25,
       units = "in",
       device = "pdf", dpi = 500)
```

## Premiums

Functions to compute the theoretical premiums.

```{r premFUN}
# Best-estimate. a is taken in argument but is not used.
BEfun <- function(pop_name, x, d, a){ 
  param <- parms[[pop_name]]
  param$b_0+param$b_d*d+param$b_x*x
}


# Unaware given A. d is taken in argument but is not used.
# a takes values 0, 1 or 2 for market
UNfun <- function(pop_name,x,d,a){
 
  param <- parms[[pop_name]]
  
  if(a==2){
    out <- param$b_0+param$b_d*ExpDgivenX(pop_name,x)+param$b_x*x
  }else{
  out <- param$b_0+param$b_d*ExpDgivenXA(pop_name,x,a)+param$b_x*x
  }
  out
}



# Aware premium given A. A=2 is the market.
AWfun <- function(pop_name,x,d,a){
  
  param <- parms[[pop_name]]
  
  if(a==2){
      out <- param$b_0+param$b_d*param$p+param$b_x*x
  }else{
  
    num <- integrate(funtointegrate1, lower=-100, upper=100, a=a,param=param)$value
    denom2 <- integrate(funtointegrate2, lower=-100, upper=100, a=a,param=param)$value
  expDgivenA <- num/(num+denom2)

  out <- param$b_0+param$b_d*expDgivenA+param$b_x*x
  }
  out
}
Vectorize(AWfun, c("x","a"))

grid_to_test2 <- expand.grid(x = unique(short_grid$x),
                             d = 0:1, 
                             a = 0:2)
```

## Corrective 

### Functions

```{r}
# Load necessary library
library(stats)

expit <- function(eta) {
        eta <- pmin(pmax(eta, -20), 20)  # Clip to avoid extreme values
        return(ifelse(eta > 0, 
                      1 / (1 + exp(-eta)), 
                      exp(eta) / (1 + exp(eta))))
      }


# Function to compute mu(X, D)
mu_X_D <- function(X, d, params) {
        params$b_0+params$b_d*d+params$b_x*X
      }

# Vectorized and compact function to compute the conditional density of X given D
conditional_density_X_given_D <- function(X, D, params) {
        
        # Extract parameters
        mu_X <- params[['g_0']]        # Mean of X (marginally Gaussian)
        sigma_X <- params[['sd_X']]  # Standard deviation of X
        rho <- params[['rho_xd']]          # Copula correlation parameter
        p_D1 <- params[['p']]        # Marginal probability of D = 1
        p_D0 <- 1 - p_D1                # Marginal probability of D = 0
        
        # Compute marginal density of X (Gaussian)
        marginal_X <- dnorm(X, mean = mu_X, sd = sigma_X)
        
        # Compute the conditional probability of D = 1 given X
        z <- (-rho * (X - mu_X)) / (sigma_X * sqrt(1 - rho^2))  # The Z-transform for the copula
        prob_D1_given_X <- 1 - pnorm(z)                            # Probability for D = 1
        prob_D0_given_X <- pnorm(z)                                # Probability for D = 0
        
        # Compute the conditional density for D = 1 and D = 0, vectorized with ifelse
        conditional_density <- ifelse(D == 1,
                                      (marginal_X * prob_D1_given_X) / p_D1,
                                      (marginal_X * prob_D0_given_X) / p_D0)
        
        return(conditional_density)
      }

# # Log-Sum-Exp Trick function
# log_sum_exp <- function(eta1, eta2) {
#         max_eta <- pmax(eta1, eta2)
#         
#         # Check if the difference is large enough to avoid computation
#         diff <- abs(eta1 - eta2)
#         
#         # Only compute the log1p part when the difference is not too large
#         result <- ifelse(diff > 30, max_eta, max_eta + log1p(exp(-diff)))
#         
#         return(result)
#       }

# Corrected smooth indicator function
smooth_indicator <- function(x, lower_bound, upper_bound, epsilon = 1e-3) {
        # Smooth transition between 0 and 1 for the lower bound
        lower_transition <- 1 / (1 + exp(-1 * (x - lower_bound) / epsilon))
        
        # Smooth transition between 1 and 0 for the upper bound
        upper_transition <- 1 / (1 + exp( (x - upper_bound) / epsilon))
        
        # The indicator is 1 inside the bounds and smoothly decays to 0 outside
        return(lower_transition * upper_transition)
      }

get_bounds_x <- function(s, d, params){
        
          lower_bound <- params[['g_0']] - 7 * params[['sd_X']]  # Typically capture ~99.999% of the distribution
          upper_bound <- params[['g_0']] + 7 * params[['sd_X']]  # Typically capture ~99.999% of the distribution
          
          if(s == Inf){
            return(c(lower_bound, upper_bound))
          } else if(params[['b_x']] > 0){
            upper_bound <- min(upper_bound, 
                                 (s - (params[['b_0']] + params[['b_d']] *
                                         d))/(params[['b_x']]) - 1e-3)
          } else if(params[['b_x']] > 0){
            lower_bound <- max(lower_bound, 
                               (s - (params[['b_0']] + params[['b_d']] *
                                       d))/(params[['b_x']]) + 1e-3)
          }
          
        return(c(lower_bound, upper_bound))
      }

pAa_XD_fun <- function(a, x, d, params){
  # Calculate components for eta_A using log-sum-exp trick
  a_0 <- -1 * (params[['a_x']] * params[['g_0']] + params[['a_d']] * params[['p']])
        
  # Instead of summing directly, apply the log-sum-exp trick
  eta_A <- a_0 + params[['a_x']] * x + params[['a_d']] * d
        
  return(ifelse(a == 1, expit(eta_A), 1 - expit(eta_A)))
}


sapply(seq(-10, 10), function(x){
  pAa_XD_fun(a = 0, x= x, d = 0, params = parms$original)
}) %>%  plot(seq(-10, 10),.)

# Function to compute eta_A using the log-sum-exp trick
int_func_gen <- function(x, d, a, s, params) {
        ## for the market : A == 2
        pAa_XD <- ifelse(a == 2, 
                     0.5, 
                     pAa_XD_fun(a = a, x = x, d = d, params = params))
        
        bounds <- get_bounds_x(s = s, d = d, params = params)
        
        smooth_indicator(x, bounds[1], bounds[2]) *
          pAa_XD *
          conditional_density_X_given_D(X = x, D = d, params)
      }

# Function to check the behavior of int_func_gen over a range of s values
check_int_func_gen_behavior <- function(s_vals, x_vals, d, a, params) {
                # Store results in a matrix to analyze
              results <- matrix(0, nrow = length(x_vals), ncol = length(s_vals))
              
              # Fill the matrix with int_func_gen evaluations
              for (i in seq_along(x_vals)) {
                for (j in seq_along(s_vals)) {
                  results[i, j] <- int_func_gen(x = x_vals[i], d = d, a = a, s = s_vals[j], params = params)
                }
              }
          
          # Visualize the results using image and contour plots
          image(x_vals, s_vals, results, main = "int_func_gen values", xlab = "x", ylab = "s")  # 's' on x-axis, 'x' on y-axis
          contour(x_vals, s_vals, results, add = TRUE, col = "blue")  # Matching axes for contour plot
            # Check the behavior at a specific x value, say x = 1
            x_fixed <- 1
            int_func_values <- sapply(s_vals, function(s) int_func_gen(x = x_fixed, d = d, a = a, s = s, params = params))
            plot(s_vals, int_func_values, type = 'b', col = "blue", main = paste("int_func_gen at x =", x_fixed),
                 xlab = "s", ylab = "int_func_gen value")
            
            # Check the behavior at a specific x value, say x = 1
            s_fixed <- 110
            int_func_values <- sapply(x_vals, function(x) int_func_gen(x = x, d = d, a = a, s = s_fixed, params = params))
            plot(x_vals, int_func_values, type = 'b', col = "blue", main = paste("int_func_gen at s =", s_fixed),
                 xlab = "x", ylab = "int_func_gen value")
          }

par(mfrow = c(2, 3))
# Test for a range of s values and x values
x_values <- seq(-7, 13, length.out = 100)
s_values <- seq(45, 150, length.out = 100)

check_int_func_gen_behavior(s_vals = s_values,
                            x_vals = x_values, d = 1, a = 1, params = parms$neutral)

check_int_func_gen_behavior(s_vals = s_values,
                            x_vals = x_values, d = 1, a = 1, params = parms$original)

par(mfrow = c(1, 1))
library(Rcpp)

# Usage
to_int_rcpp <- function(s, d, a, params) {
        
        cppFunction("
          double integrate_cpp(NumericVector x_vals, NumericVector y_vals) {
            int n = x_vals.size();
            double sum = 0.0;
            for (int i = 1; i < n; ++i) {
              sum += (x_vals[i] - x_vals[i-1]) * (y_vals[i] + y_vals[i-1]) / 2.0;
            }
            return sum;
          }
        ")
        
        bounds_num <- get_bounds_x(s = s, d = d,
                                   params = params)
        
        x_vals <- seq(bounds_num[1], bounds_num[2],
                      length.out = 1000)
        
        y_vals <- sapply(x_vals,
                         function(x) int_func_gen(x, d = d,
                                                  a = a, s = s,
                                                  params = params))
          
          max(integrate_cpp(x_vals, y_vals), 1e-10)
        }

precompute_denominator <- function(d, a, params) {
          to_int_rcpp(s = 200, d = d,
                      a = a, params = params)
        }


estimate_cdf <- function(s, d, a, params, denominator) {
            # Compute dynamic integration bounds based on X's properties
            bounds <- get_bounds_x(s = s, d = d, params = params)
            
            # Recompute denominator dynamically if needed
            if (missing(denominator) || is.null(denominator)) {
              denominator <- precompute_denominator(d = d,
                                                    a = a,
                                                    params = params)
            }
            
            # Integration with tighter tolerance and better bounds
            numerator <- to_int_rcpp(s = s, d = d,
                                     a = a, params = params)
            
            return(exp(log(numerator) - 
                         log(denominator)))
          }

# Optimized function to invert the CDF (Quantile function F^-1_S|D,A)
quantile_function <- function(prob, d, a, params, denominator, tol = 1e-6, max_iter = 150) {
  
  # CDF function that will be inverted
  cdf_function <- function(s) {
    return(estimate_cdf(s = s, d = d, a = a, params = params, denominator = denominator))
  }
  
  clipped_prob <- max(min(prob, 1 - 1e-5), 1e-5)
  
  # Root-finding for the quantile (inverse of CDF)
  cdf_diff <- function(s) {
    return(cdf_function(s) - prob)
  }
  
  # Use uniroot to find the quantile (inverse of CDF) within the bounds [50, 150]
  quantile_result <- uniroot(cdf_diff, lower = 25, upper = 200, tol = tol, maxiter = max_iter)
  
  return(quantile_result$root)
}


corr <- function(x, d, a, params, p1a){
  ## the best estimate score
  the_score <- mu_X_D(x, d, params)
  
  ## one u only 
  u <- estimate_cdf(s = the_score, d = d,
                          a = a,
                          params = params)
  
  ## push the u on every possible d
  the_transported <- sapply(0:1, function(d_alt){
    denom <- precompute_denominator(d = d_alt, a = a, params = params)
    quantile_function(prob = u, d = d_alt, a = a, params = params,
                      denominator = denom)
  })
  
  ## agregate
  return(
  (1 - p1a) * the_transported[1] +
    p1a * the_transported[2]
  )
}

```

### The corrective function

```{r}
make_corr_theo_grid <- function(scenario_name){
message1 <- paste0('--- SCENARIO : ', scenario_name, ' ---')
print(message1)
parameters <- parms[[scenario_name]]
my_corr_grid <- grid_to_test2

lil_table <- my_corr_grid %>% 
  dplyr::select(d, a) %>% 
  distinct() %>% 
  mutate(denom = sapply(1:length(d), function(i){
    precompute_denominator(d = d[i],
                           a = a[i],
                           params = parameters)
    })
    )

## add denom
my_corr_grid <- left_join(my_corr_grid, lil_table,
                          by = c('a', 'd'))

## add P(D = 1|a)
my_corr_grid <- left_join(my_corr_grid, lil_table %>% 
                            filter(d == 1) %>% 
                            rename(p1a = denom) %>% 
                            dplyr::select(a, p1a),
                          by = 'a')

## add p1
my_corr_grid$p <- parameters$p

## calculate best (exact)
my_corr_grid$best <- 1:nrow(my_corr_grid) %>% sapply(function(i){
 mu_X_D(X = my_corr_grid[i, 'x'],
        d = my_corr_grid[i, 'd'],
        params = parameters)
})

message2 <- paste0('Computing F_S|D')
print(message2)
## calculate F(S|D)
my_corr_grid$u <- 1:nrow(my_corr_grid) %>% sapply(function(i){
  message <- paste0(i, '/', nrow(my_corr_grid), ': ',
  'a = ', my_corr_grid[i, 'a'],
  ', d = ', my_corr_grid[i, 'd'],
  ', x = ', round(my_corr_grid[i, 'x'], 1))
  print(message)
  ## one u only 
  estimate_cdf(s = my_corr_grid[i, 'best'],
                        d = my_corr_grid[i, 'd'],
                        a = my_corr_grid[i, 'a'],
               denominator = my_corr_grid[i, 'denom'],
                        params = parameters)
})

my_corr_grid <- my_corr_grid %>% 
  filter(u > 1e-6, u <= 1 - 1e-6)

message3 <- paste0('Transporting to D=0')
print(message3)
my_corr_grid$moved0 <- 1:nrow(my_corr_grid) %>% sapply(function(i){
  message <- paste0(i, '/', nrow(my_corr_grid), ': ',
  'a = ', my_corr_grid[i, 'a'],
  ', u = ', round(my_corr_grid[i, 'u'], 2),
  ', d = ', my_corr_grid[i, 'd'],
  ', x = ', round(my_corr_grid[i, 'x'], 1))
  print(message)
  
  the_denom0 <- precompute_denominator(d = 0,
                                  a = my_corr_grid[i, 'a'],
                                  params = parameters)
  quantile_function(prob = my_corr_grid[i, 'u'],
                    d = 0, a = my_corr_grid[i, 'a'],
                    params = parameters,
                      denominator = the_denom0)

})

message4 <- paste0('Transporting to D=1')
print(message4)
my_corr_grid$moved1 <- 1:nrow(my_corr_grid) %>% sapply(function(i){
  message <- paste0(i, '/', nrow(my_corr_grid), ': ',
  'a = ', my_corr_grid[i, 'a'],
  ', u = ', round(my_corr_grid[i, 'u'], 2),
  ', d = ', my_corr_grid[i, 'd'],
  ', x = ', round(my_corr_grid[i, 'x'], 1))
  print(message)
  
  the_denom1 <- precompute_denominator(d = 1,
                                  a = my_corr_grid[i, 'a'],
                                  params = parameters)
  quantile_function(prob = my_corr_grid[i, 'u'],
                    d = 1, a = my_corr_grid[i, 'a'],
                    params = parameters,
                      denominator = the_denom1)

})


my_corr_grid$corr_ptf <- with(my_corr_grid, moved0 * (1 - p1a) +
                                moved1 * p1a)

my_corr_grid$corr_mprop <- with(my_corr_grid, moved0 * (1 - p) +
                                moved1 * p)

return(my_corr_grid)
}
```

### The corrective building

(focus on the long calculus to get the corrective table per insurer.)
```{r}
## long...
file_corrective  <- 'preds/corrective_tables.json'
folder_path <- "preds/"

if (!dir.exists(folder_path)) {
  dir.create(folder_path, recursive = TRUE)
}



if(file.exists(file_corrective)){ # load
  the_corr_grids_temp <- jsonlite::fromJSON(file_corrective)
} else { # simulate and write
  
  the_corr_grids_temp <- setNames(nm = names(parms)[1:3]) %>%
  lapply(function(pop_name){
    grid <- make_corr_theo_grid(scenario_name = pop_name)
    return(grid)
  })
  the_corr_grids_temp %>% jsonlite::toJSON(., pretty = TRUE) %>% write(file_corrective)
}
```

Add market expected premiums. 

```{r}
the_corr_grids <- setNames(nm = names(the_corr_grids_temp)) %>% lapply(function(grid_name){
    
  grid <- the_corr_grids_temp[[grid_name]]
    
    ## add propensity to end up with insurer 1
    grid$pA1_XD <- sapply(1:nrow(grid), function(i){
      pAa_XD_fun(a = 1,
                 x = grid[i, 'x'],
                 d = grid[i, 'd'],
                 params = parms[[grid_name]])
    })
      
    ## play around with the format of the table
    grid2 <- grid  %>% 
      dplyr::select(pA1_XD, x, d, a, p, corr_ptf) %>%
      dplyr::filter(a != 2) %>% 
  pivot_wider(names_from = a,
              values_from = corr_ptf,
              names_prefix = 'a')
    
    ## create E_A(mu^C(x, d|A)|x, d)
    grid2$mark_exp_corr <- grid2[["a0"]] * (1 - grid2$pA1_XD) + grid2[["a1"]] * grid2$pA1_XD
    
    grid3 <- grid  %>% 
      dplyr::select(pA1_XD, x, d, a, p, corr_mprop) %>%
      dplyr::filter(a != 2) %>% 
  pivot_wider(names_from = a,
              values_from = corr_mprop,
              names_prefix = 'a')
    
    ## create E_A(mu^{C*}_A(x, d)|x, d)
    grid3$mark_exp_corr_mprop <- grid3[["a0"]] * (1 - grid3$pA1_XD) + grid3[["a1"]] * grid3$pA1_XD
    
    ## left join to get the expected premium function of (x,d)
    grid <- grid %>% left_join(., grid2 %>% 
                         dplyr::select(x, d, mark_exp_corr),
                       by = c('x', 'd'))
    
    ## left join to get the expected premium* function of (x,d)
    grid <- grid %>% left_join(., grid3 %>% 
                         dplyr::select(x, d, mark_exp_corr_mprop),
                       by = c('x', 'd'))
})

```

### Graphs

```{r}
(to_save_theo_corr_prem_marketprop_temp <- names(parms)[1:3] %>% 
  lapply(function(pop_name){
    premDat <- the_corr_grids[[pop_name]] %>% 
      mutate(corr_ptf2 = corr_mprop,
             best2 = best) %>% 
      reshape2::melt(measure.vars = c('corr_mprop', 'best')) %>%
      mutate(diff = abs(d - ExpDgivenX(pop_name, x)))
    
    suppressWarnings(premDat$value[premDat$variable == 'best'][premDat$diff > 0.999] <- NA)
    suppressWarnings(premDat$value[premDat$variable == 'corr_ptf'][premDat$diff > 0.999] <- NA)  
      
    ## the colors
    premDat$a <- factor(premDat$a)
    levels(premDat$a) <- c("A=0", "A=1", "market")
    
    ## Make sure to keep the right order
    premDat$a <- factor(premDat$a, levels=names(colors_for_gg_market)) 
    
    pop_id <- which(names(sims) == pop_name)
    
    # keep only axis for last plot
    if(which(pop_name == names(sims)) == 1){
      the_y_label <- latex2exp::TeX("$\\mu^{C *}_{A}$(x, d)")
      the_x_label <- latex2exp::TeX("$x$")
    } else { # If it's on the left, apply correct xlabels
      the_y_label <- NULL
      the_x_label <- latex2exp::TeX("$x$")
    }
      
    
    premDat[c(which(premDat$variable=="corr_mprop"),
              which(premDat$variable=="best"& premDat$a==2)),] %>%
      ggplot(aes(x = x, y = value, col=factor(d), linetype=a,
                 alpha=a, linewidth=a)) + 
      geom_line() +
      scale_color_manual(values = colors_for_gg_D, name = "d")+
    scale_linetype_manual(values = c('solid','11','53'), name = "A")+
       scale_linewidth_manual(values = c(1.2,  0.65, 0.50), name = 'A')+
      scale_alpha_manual(values=c(0.25, 0.65, 0.8), name="A")+
      theme_classic() +
  labs(x = the_x_label,
       y = the_y_label,
       title = latex2exp::TeX(long_labels_for_parms[pop_id])) + 
      scale_x_continuous(breaks = c(-3:3)*3 + 1)+
      scale_y_continuous(breaks = c(90, 110, 130),
                         limits = c(80, 140)) + 
      theme(plot.title = element_text(hjust=0.5))
  }))
 
 (to_save_theo_corr_prem_marketprop <- to_save_theo_corr_prem_marketprop_temp %>% ggpubr::ggarrange(plotlist = .,
                           nrow = 1, ncol=3,
                           widths = 15, heights = 1,
                           common.legend = T,
                           legend = 'right'))

ggsave(filename = "figs/graph_prem_theo_corr_marketprop.pdf",
       plot = to_save_theo_corr_prem_marketprop,
       height = 2.75,
       width = 8,
       units = "in",
       device = "pdf", dpi = 500)
```


```{r}
(to_save_theo_corr_prem_temp <- names(parms)[1:3] %>% 
  lapply(function(pop_name){
    premDat <- the_corr_grids[[pop_name]] %>% 
      mutate(corr_ptf2 = corr_ptf,
             best2 = best) %>% 
      reshape2::melt(measure.vars = c('corr_ptf', 'best')) %>%
      mutate(diff = abs(d - ExpDgivenX(pop_name, x)))
    
    suppressWarnings(premDat$value[premDat$variable == 'best'][premDat$diff > 0.999] <- NA)
    suppressWarnings(premDat$value[premDat$variable == 'corr_ptf'][premDat$diff > 0.999] <- NA)  
      
    ## the colors
    premDat$a <- factor(premDat$a)
    levels(premDat$a) <- c("A=0", "A=1", "market")
    
    ## Make sure to keep the right order
    premDat$a <- factor(premDat$a, levels=names(colors_for_gg_market)) 
    
    pop_id <- which(names(sims) == pop_name)
    
    # keep only axis for last plot
    if(which(pop_name == names(sims)) == 1){
      the_y_label <- latex2exp::TeX("$\\mu^C(x, d, A)$")
      the_x_label <- latex2exp::TeX("$x$")
    } else { # If it's on the left, apply correct xlabels
      the_y_label <- NULL
      the_x_label <- latex2exp::TeX("$x$")
    }
      
    
    premDat[c(which(premDat$variable=="corr_ptf"),
              which(premDat$variable=="best"& premDat$a==2)),] %>%
      ggplot(aes(x = x, y = value, col=factor(d), linetype=a,
                 alpha=a, linewidth=a)) + 
      geom_line() +
      scale_color_manual(values = colors_for_gg_D, name = "d")+
    scale_linetype_manual(values = c('solid','12','53'), name = "A")+
       scale_linewidth_manual(values = c(1.2,  0.65, 0.50), name = 'A')+
      scale_alpha_manual(values=c(0.25, 0.65, 0.8), name="A")+
      theme_classic() +
  labs(x = the_x_label,
       y = the_y_label,
       title = latex2exp::TeX(long_labels_for_parms[pop_id])) + 
      scale_x_continuous(breaks = c(-3:3)*3 + 1)+
      theme(plot.title = element_text(hjust=0.5)) + 
      scale_y_continuous(breaks = c(90, 110, 130),
                         limits = c(70, 150))
    
  }))
 
 
 (to_save_theo_corr_prem <- to_save_theo_corr_prem_temp %>% ggpubr::ggarrange(plotlist = .,
                           nrow = 1, ncol=3,
                           widths = 15, heights = 1,
                           common.legend = T,
                           legend = 'right'))

ggsave(filename = "figs/graph_prem_theo_corr.pdf",
       plot = to_save_theo_corr_prem,
       height = 2.75,
       width = 8,
       units = "in",
       device = "pdf", dpi = 500)
```

```{r}
compute_conditional_cdfs <- function(params, s_values) {
  
  ## Extract parameters
  gamma_0 <- params[['g_0']]
  beta_0 <- params[['b_0']]
  beta_x <- params[['b_x']]
  beta_d <- params[['b_d']]
  sigma_x <- params[['sd_X']]
  rho <- params[['rho_xd']]
  
  ## Copula (X, D)
  Phi <- pnorm(((s_values - beta_0) / beta_x - gamma_0)/sigma_x)
  u <- matrix(c(rep(0.5, length(Phi)), Phi), byrow = FALSE, ncol = 2)
  cop <- copula::pCopula(u, copula= copula::normalCopula(param = rho))
  
  ## Compute F_{S|D}(s|0)
  compute_FSD <- function(d) {
    if(d == 0){
     to_return <- 2 * cop 
    } else if(d == 1){
      to_return <- 2 * (Phi - cop)
    }
    return(to_return)
  }
  
  ## Apply to all s values
  FSD_0_values <- compute_FSD(d = 0)
  FSD_1_values <- compute_FSD(d = 1)
  FSD_values <- (FSD_0_values + FSD_1_values)/2
  
  h <- s_values[2] - s_values[1]
  
  fSD_0_values <- c(0, (tail(FSD_0_values, -1) -  head(FSD_0_values, -1))/h)
  fSD_1_values <- c(0, (tail(FSD_1_values, -1) -  head(FSD_1_values, -1))/h)
  fSD_values <-c(0, (tail(FSD_values, -1) -  head(FSD_values, -1))/h)
  
  ## Return results as data frame
  results <- data.frame('s' = s_values, 
                        'FSD_0' = FSD_0_values, 
                        'FSD_1' = FSD_1_values,
                        'FSD' = FSD_values,
                        'fSD_0' = fSD_0_values,
                        'fSD_1' = fSD_1_values,
                        'fSD' = fSD_values)
  
  return(results)
}

s_values <- seq(70, 135, by = 0.2)

the_df <- compute_conditional_cdfs(params = parms$original, s_values)

sapply(0:1, function(i){
  lvls <- c('best', 'corr_ptf')
  
    premDat <- the_corr_grids[['original']] %>% 
      mutate(corr_ptf2 = corr_ptf,
             best2 = best) %>% 
      reshape2::melt(measure.vars = lvls[1:(1 + i)]) %>%
      mutate(diff = abs(d - ExpDgivenX('original', x)))


    suppressWarnings(premDat$value[premDat$variable == 'best'][premDat$diff > 0.999] <- NA)
    suppressWarnings(premDat$value[premDat$variable == 'corr_ptf'][premDat$diff > 0.999] <- NA)  
      
    ## the colors
    premDat$a <- factor(premDat$a)
    levels(premDat$a) <- c("A=0", "A=1", "market")
    
    ## Make sure to keep the right order
    premDat$a <- factor(premDat$a, levels=names(colors_for_gg_market)) 

to_g_arrows <- premDat %>%
  filter(a == 'market') %>% 
  mutate(extreme = ((u < 0.06)&d==0)|((u > 0.93)&d==1)) 
  


  s_values <- the_df$s
fSD_0_values <- the_df$fSD_0
fSD_1_values <- the_df$fSD_1
fSD_values <- the_df$fSD

 if(i == 0){
   the_arrows1 <- NULL
    the_arrows2 <- NULL
  } else {
    the_arrows1 <- geom_segment(data = to_g_arrows %>% 
                     filter(extreme),
              aes(x = x, xend = x, y = best2, yend = corr_ptf2),
                   arrow = arrow(length = unit(0.2, "cm")),
              lwd = 0.6, lty = 1, alpha = 0.3)
    
    the_arrows2 <- geom_segment(data = data.frame(s = c(s_values[min(which(the_df$fSD_0 > 0.035))],
                                                       s_values[max(which(the_df$fSD_1 > 0.035))]),
                                                 d = c(0, 1),
                                                 send = c(s_values[min(which(the_df$fSD > 0.035))],
                                                       s_values[max(which(the_df$fSD > 0.035))]),
                                                 dens = c(0.035, 0.035),
                                                 densend = c(0.035, 0.035)),
              aes(x = s, xend = send, y = dens, yend = densend),
                   arrow = arrow(length = unit(0.2, "cm")),
              lwd = 0.6, lty = 1, alpha = 0.6)
  }
  
g1 <- to_g_arrows %>% 
  mutate(variable = factor(variable,
                           levels = lvls[1:(1 + i)])) %>% 
      ggplot(aes(x = x, y = value, col=factor(d), linetype=factor(variable),
                 alpha=factor(variable), linewidth=factor(d))) + 
      geom_line() +
      the_arrows1 +
      scale_color_manual(values = colors_for_gg_D, name = "d")+
    scale_linetype_manual(values = c(3, 1), name = "S(x, d)", labels = unname(c(latex2exp::TeX("$\\mu(x, d)$"), latex2exp::TeX("$\\mu^C(x, d)$")))) +
       scale_linewidth_manual(values = c(1.1, 0.75), name = 'd') +
      scale_alpha_manual(values=c(0.25, 1), name = 'S(x, d)', labels = unname(c(latex2exp::TeX("$\\mu(x, d)$"), latex2exp::TeX("$\\mu^C(x, d)$")))) +
      theme_classic() +
  labs(x = latex2exp::TeX("$x$"),
       y = latex2exp::TeX("$S(x, d)$")) + 
      scale_x_continuous(breaks = c(-3:3)*3 + 1)+
      theme(plot.title = element_text(hjust=0.5))+
  guides(
    col = guide_legend(nrow = 2, order = 1),  # Control number of columns for consistency
    linewidth = guide_legend(nrow = 2, order = 1),
    lty = guide_legend(nrow = 2, order = 2),
    alpha = guide_legend(nrow = 2, order = 2)
  )


g2 <- data.frame('d' = c(rep(0, length(s_values)),
                   rep(1, length(s_values)),
                   rep(0, length(s_values)),
                   rep(1, length(s_values))),
           'prem' = c(rep('best', length(s_values) * 2),
                   rep('corr', length(s_values) * 2)),
           'dens' = c(fSD_0_values, fSD_1_values,
                      fSD_values, fSD_values),
           's' = rep(s_values, 4))[1:(length(s_values) * 2 * (1 + i)), ] %>% 
  ggplot(aes(x = s, y = dens, 
             col=factor(d), 
             linetype=factor(prem),
             alpha=factor(prem),
             linewidth=factor(d))) + 
  geom_line(alpha = 0.5) + 
  the_arrows2 + 
  scale_color_manual(values = colors_for_gg_D, name = "d")+
    scale_linetype_manual(values = c(3, 1), name = "S(x, d)", labels = unname(c(latex2exp::TeX("$\\mu(x, d)$"), latex2exp::TeX("$\\mu^C(x, d)$"))[1:(1 + i)])) +
       scale_linewidth_manual(values = c(1.2, 0.6), name = 'd') +
      scale_alpha_manual(values=c(0.35, 1), name = 'S(x, d)', labels = unname(c(latex2exp::TeX("$\\mu(x, d)$"), latex2exp::TeX("$\\mu^C(x, d)$"))[1:(1 + i)])) +
      theme_classic() +
  labs(x = latex2exp::TeX("$s$"),
       y = latex2exp::TeX("$f_{S|D}(s|d)$")) + 
      theme(plot.title = element_text(hjust=0.5)) +
  guides(
    col = guide_legend(nrow = 2, order = 1),  # Control number of columns for consistency
    linewidth = guide_legend(nrow = 2, order = 1),
    lty = guide_legend(nrow = 2, order = 2),
    alpha = guide_legend(nrow = 2, order = 2)
  )
  
  
  ggpubr::ggarrange(g1, g2, common.legend = T,
                    legend = 'right') %>% 
ggsave(filename = paste0("figs/graph_corr_illustration_", i, ".pdf"),
       plot = .,
       height = 2.75,
       width = 7,
       units = "in",
       device = "pdf", dpi = 500)
})

```


## Plots

We are ready to plot the theoretical curves.

First, the unaware premiums:

```{r graphunaware, echo=FALSE, fig.width=12, fig.height=4}


(to_save_theo_unaware_prem <- names(parms)[1:3] %>% 
  lapply(function(pop_name){
    premDat <- grid_to_test2 %>% 
      mutate(best = sapply(1:nrow(grid_to_test2), function(i){
        BEfun(pop_name, x= grid_to_test2[i, 'x'],
                 d = grid_to_test2[i, 'd'],
                 a = grid_to_test2[i, 'a'])}),
              un = sapply(1:nrow(grid_to_test2), function(i){
        UNfun(pop_name,
              x=grid_to_test2[i, 'x'],
              d=grid_to_test2[i, 'd'],
              a=grid_to_test2[i, 'a'])})) %>% 
      reshape2::melt(measure.vars = c('best', 'un'))%>%
      mutate(diff = abs(d - ExpDgivenX(pop_name, x)))
    
    suppressWarnings(premDat$value[premDat$variable == 'best'][premDat$diff > 0.999] <- NA)
      
      
    ## the colors
    premDat$a <- factor(premDat$a)
    levels(premDat$a) <- c("A=0", "A=1", "market")
    
    ## Make sure to keep the right order
    premDat$a <- factor(premDat$a, levels=names(colors_for_gg_market)) 
    
    pop_id <- which(names(sims) == pop_name)
    
    # keep only axis for last plot
    if(which(pop_name == names(sims)) == 1){
      the_y_label <- latex2exp::TeX("Unaware Premium")
      the_x_label <- latex2exp::TeX("$x$")
    } else { # If it's on the left, apply correct xlabels
      the_y_label <- NULL
      the_x_label <- latex2exp::TeX("$x$")
    }
      
    
    premDat[c(which(premDat$variable=="un"&premDat$d==1)),]%>%
      ggplot(aes(x = x, y = value, col=a, linetype=a,
                 alpha=variable, linewidth=factor(d))) + 
      geom_line(data = premDat[c(which(premDat$variable=="best"&premDat$a=="market")),],
                linetype = 1, color = 'black', alpha = 0.6) + 
      geom_line() +
      scale_color_manual(values = colors_for_gg_market, name = "A")+
    scale_linetype_manual(values = c(1,3,2), name = "A")+
       scale_linewidth_manual(values = setNames(c(1.2, 0.65), nm = c('0', '1')), name = 'd')+
      scale_alpha_manual(values=c(0.8,0.9), guide="none")+
      theme_classic() +
  labs(x = the_x_label,
       y = the_y_label,
       title = latex2exp::TeX(long_labels_for_parms[pop_id])) + 
      scale_x_continuous(breaks = c(-3:3)*3 + 1)+
      theme(plot.title = element_text(hjust=0.5))
  }) %>% ggpubr::ggarrange(plotlist = .,
                           nrow = 1, ncol=3,
                           widths = 15, heights = 1,
                           common.legend = T,
                           legend = 'right'))

ggsave(filename = "figs/graph_prem_theo_unaware.pdf",
       plot = to_save_theo_unaware_prem,
       height = 2.75,
       width = 8,
       units = "in",
       device = "pdf", dpi = 500)
```

Then the aware premiums. For the next graph, consider cutting the lines when Prob(A=a) is small.

```{r graphaware, echo=FALSE, fig.width=12, fig.height=4}

(to_save_theo_aware_prem <- names(parms)[1:3] %>% 
  lapply(function(pop_name){
    premDat <- grid_to_test2 %>% 
      mutate(best = sapply(1:nrow(grid_to_test2), function(i){
        BEfun(pop_name, x= grid_to_test2[i, 'x'],
                 d = grid_to_test2[i, 'd'],
                 a = grid_to_test2[i, 'a'])}),
             aw = sapply(1:nrow(grid_to_test2), function(i){
        AWfun(pop_name,
              x=grid_to_test2[i, 'x'],
              d=grid_to_test2[i, 'd'],
              a=grid_to_test2[i, 'a'])})) %>% 
      reshape2::melt(measure.vars = c('best', 'aw'))%>%
      mutate(diff = abs(d - ExpDgivenX(pop_name, x)))
    
    suppressWarnings(premDat$value[premDat$variable == 'best'][premDat$diff > 0.999] <- NA)
      
      
    ## the colors
    premDat$a <- factor(premDat$a)
    levels(premDat$a) <- c("A=0", "A=1", "market")
    
    ## Make sure to keep the right order
    premDat$a <- factor(premDat$a, levels=names(colors_for_gg_market)) 
    
    pop_id <- which(names(sims) == pop_name)
    
    # keep only axis for last plot
    if(which(pop_name == names(sims)) == 1){
      the_y_label <- latex2exp::TeX("Aware Premium")
      the_x_label <- latex2exp::TeX("$x$")
    } else { # If it's on the left, apply correct xlabels
      the_y_label <- NULL
      the_x_label <- latex2exp::TeX("$x$")
    }
      
    
    premDat[c(which(premDat$variable=="aw"&premDat$d==1)),]%>%
      ggplot(aes(x = x, y = value, col=a, linetype=a,
                 alpha=variable, linewidth=factor(d))) + 
      geom_line(data = premDat[c(which(premDat$variable=="best"&premDat$a=="market")),],
                linetype = 1, color = 'black', alpha = 0.6) + 
      geom_line() +
      scale_color_manual(values = colors_for_gg_market, name = "A")+
    scale_linetype_manual(values = c(1,3,2), name = "A")+
       scale_linewidth_manual(values = setNames(c(1.2, 0.65), nm = c('0', '1')), name = 'd')+
      scale_alpha_manual(values=c(0.8,0.9), guide="none")+
      theme_classic() +
  labs(x = the_x_label,
       y = the_y_label,
       title = latex2exp::TeX(long_labels_for_parms[pop_id])) + 
      scale_x_continuous(breaks = c(-3:3)*3 + 1)+
      theme(plot.title = element_text(hjust=0.5))
  }) %>% ggpubr::ggarrange(plotlist = .,
                           nrow = 1, ncol=3,
                           widths = 15, heights = 1,
                           common.legend = T,
                           legend = 'right'))

ggsave(filename = "figs/graph_prem_theo_aware.pdf",
       plot = to_save_theo_aware_prem,
       height = 2.75,
       width = 8,
       units = "in",
       device = "pdf", dpi = 500)
```

Plot for graphical abstract scenario A only

```{r graphawareScA, echo=FALSE, fig.width=12, fig.height=4}


  
  pop_name <- names(parms)[1]

    premDat <- grid_to_test2 %>% 
      mutate(best = sapply(1:nrow(grid_to_test2), function(i){
        BEfun(pop_name, x= grid_to_test2[i, 'x'],
                 d = grid_to_test2[i, 'd'],
                 a = grid_to_test2[i, 'a'])}),
             aw = sapply(1:nrow(grid_to_test2), function(i){
        AWfun(pop_name,
              x=grid_to_test2[i, 'x'],
              d=grid_to_test2[i, 'd'],
              a=grid_to_test2[i, 'a'])})) %>% 
      reshape2::melt(measure.vars = c('best', 'aw'))%>%
      mutate(diff = abs(d - ExpDgivenX(pop_name, x)))
    
    suppressWarnings(premDat$value[premDat$variable == 'best'][premDat$diff > 0.999] <- NA)
  

    ## the colors
    premDat$a <- factor(premDat$a)
    levels(premDat$a) <- c("A=0", "A=1", "market")
    
    ## Make sure to keep the right order
    premDat$a <- factor(premDat$a, levels=names(colors_for_gg_market)) 
    
    pop_id <- which(names(sims) == pop_name)
    
premDat <- premDat[c(which(premDat$variable=="aw"&premDat$d==1),
              which(premDat$variable=="best"&premDat$a=="market")),]

newlab <- as.integer(premDat$a)
newlab[which(premDat$variable=="best")] <- 4+premDat$d[which(premDat$variable=="best")]

newlab <- factor(newlab)
levels(newlab) <- c(levels(premDat$a), c("E(Y|x,d=0)", "E(Y|x,d=1)"))

    # keep only axis for last plot
    if(which(pop_name == names(sims)) == 1){
      the_y_label <- latex2exp::TeX("Aware Premium")
      the_x_label <- latex2exp::TeX("$x$")
    } else { # If it's on the left, apply correct xlabels
      the_y_label <- NULL
      the_x_label <- latex2exp::TeX("$x$")
    }

premDat$newlab <- newlab
    
(to_save_theo_aware_prem_ScA <- 
      ggplot(premDat, aes(x = x, y = value, col=newlab, linetype=newlab, linewidth=newlab)) + 
      geom_line() +
      scale_color_manual(values = c(unname(colors_for_gg_market),"black", "black"), name = "")+
    scale_linetype_manual(values = c(1,3,2,1,4), name = "")+
    scale_linewidth_manual(values = c(1, 1,1,1.1,1.1), name = '')+
      theme_classic() +
  labs(x = the_x_label,
       y = the_y_label) + 
      scale_x_continuous(breaks = c(-3:3)*3 + 1)+
  theme(panel.background=element_rect(fill="transparent"),
        plot.background = element_rect(fill='transparent', color=NA),
        legend.background = element_rect(fill='transparent'),
        legend.position=c(0.9,0.3),
  plot.margin=margin(5.5,30,5.5,5.5)))
  

ggsave(filename = "figs/graph_theo_aware_prem_ScA.pdf",
       plot = to_save_theo_aware_prem_ScA,
       height = 2.9,
       width = 3,
       units = "in",
       device = "pdf", dpi = 500)
```

### Expected premiums

Now, we consider the expected price from the perspective of the insured, given D=0 or D=1.

```{r expectedpremfun}

pAgivenXD <- function(x,d,a, param){
   a_0 <- -1 * sum(param[['a_x']]*param[['g_0']] + param[['a_d']] * param[['p']])
 
(exp(a_0+param[['a_x']]*x+param[['a_d']]*d))^(a==1)/(1+exp(a_0+param[['a_x']]*x+param[['a_d']]*d))
}

un_fun_market <- function(pop_name, x, d){
  param <- parms[[pop_name]]
  pAgivenXD(x, d, 1, param) * UNfun(pop_name,x=x, d=d, a=1) +
  pAgivenXD(x, d, 0, param) * UNfun(pop_name,x=x, d=d, a=0)
}

aw_fun_market <- function(pop_name, x, d){
  param <- parms[[pop_name]]
  pAgivenXD(x, d, 1, param) * AWfun(pop_name, x=x, d=d, a=1) +
  pAgivenXD(x, d, 0, param) * AWfun(pop_name, x=x, d=d, a=0)
}
```

We can plot everything on the same graph.

```{r graphblackandwhite, fig.height=4, fig.width=10, echo=FALSE}
(to_save_theo_prem_fullpop <- names(parms)[names(parms) %in% c("original", "neutral", "noDtoA")] %>% 
  lapply(function(pop_name){
    short_grid <- grid_to_test2 %>% 
      filter(a == 1)
    
    premDat <- short_grid %>% 
      mutate(best = sapply(1:nrow(short_grid), function(i){
        BEfun(pop_name,
              x=short_grid[i, 'x'],
              d=short_grid[i, 'd'],
                a=1)}),
        un = sapply(1:nrow(short_grid), function(i){
        un_fun_market(pop_name,
                      x=short_grid[i, 'x'],
                 d=short_grid[i, 'd'])}),
        aw = sapply(1:nrow(short_grid), function(i){
        aw_fun_market(pop_name,
                      x=short_grid[i, 'x'],
                      d=short_grid[i, 'd'])})) %>% 
      reshape2::melt(measure.vars = c('best', 'un', 'aw'))
    
    pop_id <- which(names(sims) == pop_name)
    
    # keep only axis for last plot
    if(which(pop_name == names(sims)) == 1){
      the_y_label <- latex2exp::TeX("Premium")
      the_y_scale <- scale_y_continuous()
      the_x_label <- latex2exp::TeX("x")
      } else { 
      the_y_label <- NULL
      the_y_scale <- scale_y_continuous(labels = NULL)
      the_x_label <- latex2exp::TeX("x")
    }
      
      
    premDat %>% ggplot(aes(x = x, y = value,
               col = variable,
               lty = factor(d),
             linewidth = factor(d),
               )) + 
      geom_line(alpha = 0.75) + 
  labs(x = the_x_label,
       y = the_y_label,
       title = latex2exp::TeX(long_labels_for_parms[pop_id])) + 
      scale_x_continuous(breaks = c(-3:3)*3 + 1)  + # see above
      the_y_scale +
  theme_minimal()+
  theme(plot.title = element_text(hjust=0.5))+
  scale_color_manual(values = c('black', head(gray.colors(3), 2)), name = "A") +
  scale_linetype_manual(values = c(1, 2), name = "d") +
  scale_linewidth_manual(values = c(1, 0.55), name = 'd') 
  }) %>% ggpubr::ggarrange(plotlist = .,
                           nrow = 1, ncol=3,
                           widths = 15, heights = 1,
                           common.legend = T,
                           legend = 'right'))

ggsave(filename = "figs/graph_prem_theo_fullpop.pdf",
       plot = to_save_theo_prem_fullpop,
       height = 3,
       width = 8,
       units = "in",
       device = "pdf", dpi = 500)

```

We can try something more lively.

```{r graphlively, fig.height=4, fig.width=10, echo=FALSE}
(to_save_theo_expected_prem <- names(parms)[names(parms) %in% c("original", "neutral", "noDtoA")] %>% 
  lapply(function(pop_name){
    short_grid <- grid_to_test2 %>% 
      filter(a == 1)
    
    the_corr_grid <- the_corr_grids[[pop_name]]
    
    premDat <- short_grid %>% 
      mutate(x = round(x, 4), 
             best = sapply(1:nrow(short_grid), function(i){
        BEfun(pop_name,
              x=short_grid[i, 'x'],
              d=short_grid[i, 'd'],
                a=1)}),
        un = sapply(1:nrow(short_grid), function(i){
        un_fun_market(pop_name,
                      x=short_grid[i, 'x'],
                 d=short_grid[i, 'd'])}),
        aw = sapply(1:nrow(short_grid), function(i){
        aw_fun_market(pop_name,
                      x=short_grid[i, 'x'],
                      d=short_grid[i, 'd'])})) %>% 
      left_join(., the_corr_grid %>% 
      dplyr::select(x, d, mark_exp_corr) %>% 
        mutate(x = round(x, 4)), 
      by = c('x', 'd')) %>% 
      mutate(corr = mark_exp_corr) %>% 
      dplyr::select(-mark_exp_corr) %>% 
      reshape2::melt(measure.vars = c('best', 'un', 'aw', 'corr'))%>%
      mutate(diff = abs(d - ExpDgivenX(pop_name, x)))
    
    suppressWarnings(premDat$value[premDat$variable == 'best'][premDat$diff > 0.999] <- NA)
    suppressWarnings(premDat$value[premDat$variable == 'un'][premDat$diff > 0.999] <- NA)
    suppressWarnings(premDat$value[premDat$variable == 'aw'][premDat$diff > 0.999] <- NA)
    suppressWarnings(premDat$value[premDat$variable == 'corr'][premDat$diff > 0.999] <- NA)
    
    pop_id <- which(names(sims) == pop_name)
    
    # keep only axis for last plot
    if(which(pop_name == names(sims)) == 1){
      the_y_label <- latex2exp::TeX("Premium")
      the_y_scale <- scale_y_continuous(breaks = c(90, 110, 130)) 
      the_x_label <- latex2exp::TeX("x")
      } else { 
      the_y_label <- NULL
      the_y_scale <- scale_y_continuous(breaks = c(90, 110, 130)) 
      the_x_label <- latex2exp::TeX("x")
    }
      
      
    premDat %>% 
      filter(variable != 'corr') %>% 
      ggplot(aes(x = x, y = value,
               col = variable,
               lty = factor(d),
             linewidth = factor(d),
             alpha=factor(d),
               )) + 
      geom_line() + 
  labs(x = the_x_label,
       y = the_y_label,
       title = latex2exp::TeX(long_labels_for_parms[pop_id])) + 
      scale_x_continuous(breaks = c(-3:3)*3 + 1)  + # see above
      the_y_scale +
  theme_classic()+
  theme(plot.title = element_text(hjust=0.5))+
  scale_color_manual(values = colors_for_gg_premium, name = "Premium") +
  scale_linetype_manual(values = c(1, 2), name = "d") +
  scale_linewidth_manual(values = c(1, 0.55), name = 'd')+
  scale_alpha_manual(values=c(0.5,1), name="d")
  }) %>% ggpubr::ggarrange(plotlist = .,
                           nrow = 1, ncol=3,
                           widths = 15, heights = 1,
                           common.legend = T,
                           legend = 'right'))

ggsave(filename = "figs/graph_theo_expected_prem.pdf",
       plot = to_save_theo_expected_prem,
       height = 2.75, #2.75,
       width = 8,
       units = "in",
       device = "pdf", dpi = 500)

```

```{r graphlively2, fig.height=4, fig.width=10, echo=FALSE}
(to_save_theo_expected_prem2 <- names(parms)[names(parms) %in% c("original", "neutral", "noDtoA")] %>% 
  lapply(function(pop_name){
    short_grid <- grid_to_test2 %>% 
      filter(a == 1)
    
    the_corr_grid <- the_corr_grids[[pop_name]]
    
    premDat <- short_grid %>% 
      mutate(x = round(x, 4), 
             best = sapply(1:nrow(short_grid), function(i){
        BEfun(pop_name,
              x=short_grid[i, 'x'],
              d=short_grid[i, 'd'],
                a=1)}),
        un = sapply(1:nrow(short_grid), function(i){
        un_fun_market(pop_name,
                      x=short_grid[i, 'x'],
                 d=short_grid[i, 'd'])}),
        aw = sapply(1:nrow(short_grid), function(i){
        aw_fun_market(pop_name,
                      x=short_grid[i, 'x'],
                      d=short_grid[i, 'd'])})) %>% 
      left_join(., the_corr_grid %>% 
      dplyr::select(x, d, mark_exp_corr) %>% 
        mutate(x = round(x, 4)), 
      by = c('x', 'd')) %>% 
      mutate(corr = mark_exp_corr) %>% 
      dplyr::select(-mark_exp_corr) %>% 
      reshape2::melt(measure.vars = c('best', 'un', 'aw', 'corr'))%>%
      mutate(diff = abs(d - ExpDgivenX(pop_name, x)))
    
    suppressWarnings(premDat$value[premDat$variable == 'best'][premDat$diff > 0.999] <- NA)
    suppressWarnings(premDat$value[premDat$variable == 'un'][premDat$diff > 0.999] <- NA)
    suppressWarnings(premDat$value[premDat$variable == 'aw'][premDat$diff > 0.999] <- NA)
    suppressWarnings(premDat$value[premDat$variable == 'corr'][premDat$diff > 0.999] <- NA)
    
    pop_id <- which(names(sims) == pop_name)
    
    # keep only axis for last plot
    if(which(pop_name == names(sims)) == 1){
      the_y_label <- latex2exp::TeX("Premium")
      the_y_scale <- scale_y_continuous(breaks = c(90, 110, 130)) 
      the_x_label <- latex2exp::TeX("x")
      } else { 
      the_y_label <- NULL
      the_y_scale <- scale_y_continuous(breaks = c(90, 110, 130)) 
      the_x_label <- latex2exp::TeX("x")
    }
      
      
    premDat %>% 
      mutate(d = factor(d, levels = 1:0, 
                        labels = c('d = 1', 'd = 0'))) %>% 
      ggplot(aes(x = x, y = value,
               col = variable,
               lty = factor(d),
             linewidth = factor(d),
             alpha=factor(d),
               )) + 
      geom_line() + 
  labs(x = the_x_label,
       y = the_y_label,
       title = latex2exp::TeX(long_labels_for_parms[pop_id])) + 
      scale_x_continuous(breaks = c(-3:3)*3 + 1)  + # see above
      the_y_scale +
  theme_classic()+
    facet_grid(rows = vars(d)) + 
  theme(plot.title = element_text(hjust=0.5))+
  scale_color_manual(values = colors_for_gg_premium, name = "Premium") +
  scale_linetype_manual(values = c(1, 2), name = "d") +
  scale_linewidth_manual(values = c(1, 0.55), name = 'd')+
  scale_alpha_manual(values=c(0.5,1), name="d")
  }) %>% ggpubr::ggarrange(plotlist = .,
                           nrow = 1, ncol=3,
                           widths = 15, heights = 1,
                           common.legend = T,
                           legend = 'right'))

ggsave(filename = "figs/graph_theo_expected_prem2.pdf",
       plot = to_save_theo_expected_prem2,
       height = 3.75, #2.75,
       width = 8,
       units = "in",
       device = "pdf", dpi = 500)

```


```{r graphlively3, fig.height=4, fig.width=10, echo=FALSE}
(to_save_theo_expected_prem3_temp <- names(parms)[names(parms) %in% c("original", "neutral", "noDtoA")] %>% 
  lapply(function(pop_name){
    
    the_corr_grid <- the_corr_grids[[pop_name]]
    
    premDat <- the_corr_grid %>% 
      filter(a == 2) %>% 
      reshape2::melt(measure.vars = c('corr_ptf',
                                      'mark_exp_corr_mprop', 'mark_exp_corr'))%>%
      mutate(diff = abs(d - ExpDgivenX(pop_name, x))
             )
    
    labels_for_the_corrs <- unname(latex2exp::TeX(c('$\\mu^C(x, d)$',
                                                                '${E_A}\\{\\mu^{C *}_A(x, d)|x, d\\}$', '${E_A} \\{\\mu^C(x, d,A)|x, d\\}$')
                                                              ))
      
    suppressWarnings(premDat$value[premDat$variable == 'corr_ptf'][premDat$diff > 0.999] <- NA)
    suppressWarnings(premDat$value[premDat$variable == 'mark_exp_corr'][premDat$diff > 0.999] <- NA)
    suppressWarnings(premDat$value[premDat$variable == 'mark_exp_corr_mprop'][premDat$diff > 0.999] <- NA)
    
    pop_id <- which(names(sims) == pop_name)
    
    # keep only axis for last plot
    if(which(pop_name == names(sims)) == 1){
      the_y_label <- latex2exp::TeX("Premium")
      the_y_scale <- scale_y_continuous(breaks = c(90, 110, 130)) 
      the_x_label <- latex2exp::TeX("x")
      } else { 
      the_y_label <- NULL
      the_y_scale <- scale_y_continuous(breaks = c(90, 110, 130)) 
      the_x_label <- latex2exp::TeX("x")
    }
      
      
    premDat %>% 
      mutate(d = factor(d, levels = 1:0, 
                        labels = c('1', '0'))) %>% 
      ggplot(aes(x = x, y = value,
               col = factor(d),
               lty = variable,
             linewidth = variable,
             alpha=variable,
               )) + 
      geom_line() + 
  labs(x = the_x_label,
       y = the_y_label,
       title = latex2exp::TeX(long_labels_for_parms[pop_id])
       ) + 
      scale_x_continuous(breaks = c(-3:3)*3 + 1)  + # see above
      the_y_scale +
  theme_classic()+
  theme(plot.title = element_text(hjust=0.5))+
  scale_color_manual(values = setNames(colors_for_gg_D, nm = c('0', '1')), name = "d") +
  scale_linetype_manual(values = c('solid', '93', '11'), name = "Premium", labels = labels_for_the_corrs) +
  scale_linewidth_manual(values = c(1.2,  0.65, 0.50), name = 'Premium', labels =labels_for_the_corrs)+
  scale_alpha_manual(values=c(0.25, 0.65, 0.8), name="Premium", labels =labels_for_the_corrs)
  })) 
 
(to_save_theo_expected_prem3 <-  to_save_theo_expected_prem3_temp %>% ggpubr::ggarrange(plotlist = .,
                           nrow = 1, ncol=3,
                           widths = 15, heights = 1,
                           common.legend = T,
                           legend = 'right'))

ggsave(filename = "figs/graph_theo_expected_prem3.pdf",
       plot = to_save_theo_expected_prem3,
       height = 2.75, #2.75,
       width = 8,
       units = "in",
       device = "pdf", dpi = 500)

```


```{r graphlively4, fig.height=4, fig.width=10, echo=FALSE}
(to_save_theo_expected_prem4 <- names(parms)[names(parms) %in% c("original", "neutral", "noDtoA")] %>% 
  lapply(function(pop_name){
    short_grid <- grid_to_test2 %>% 
      filter(a == 1)
    
    the_corr_grid <- the_corr_grids[[pop_name]]
    
    premDat <- short_grid %>% 
      mutate(x = round(x, 4), 
             best = sapply(1:nrow(short_grid), function(i){
        BEfun(pop_name,
              x=short_grid[i, 'x'],
              d=short_grid[i, 'd'],
                a=1)}),
        un = sapply(1:nrow(short_grid), function(i){
        un_fun_market(pop_name,
                      x=short_grid[i, 'x'],
                 d=short_grid[i, 'd'])}),
        aw = sapply(1:nrow(short_grid), function(i){
        aw_fun_market(pop_name,
                      x=short_grid[i, 'x'],
                      d=short_grid[i, 'd'])})) %>% 
      left_join(., the_corr_grid %>% 
      dplyr::select(x, d, mark_exp_corr) %>% 
        mutate(x = round(x, 4)), 
      by = c('x', 'd')) %>% 
      mutate(corr = mark_exp_corr) %>% 
      dplyr::select(-mark_exp_corr) %>% 
      reshape2::melt(measure.vars = c('best', 'un', 'aw', 'corr'))%>%
      mutate(diff = abs(d - ExpDgivenX(pop_name, x)))
    
    suppressWarnings(premDat$value[premDat$variable == 'best'][premDat$diff > 0.999] <- NA)
    suppressWarnings(premDat$value[premDat$variable == 'un'][premDat$diff > 0.999] <- NA)
    suppressWarnings(premDat$value[premDat$variable == 'aw'][premDat$diff > 0.999] <- NA)
    suppressWarnings(premDat$value[premDat$variable == 'corr'][premDat$diff > 0.999] <- NA)
    
    pop_id <- which(names(sims) == pop_name)
    
    # keep only axis for last plot
    if(which(pop_name == names(sims)) == 1){
      the_y_label <- latex2exp::TeX("Premium")
      the_y_scale <- scale_y_continuous(breaks = c(90, 110, 130)) 
      the_x_label <- latex2exp::TeX("x")
      } else { 
      the_y_label <- NULL
      the_y_scale <- scale_y_continuous(breaks = c(90, 110, 130)) 
      the_x_label <- latex2exp::TeX("x")
    }
      
      
    premDat %>% 
      mutate(d = factor(d, levels = 1:0, 
                        labels = c('d = 1', 'd = 0'))) %>% 
      ggplot(aes(x = x, y = value,
               col = variable,
               lty = factor(d),
             linewidth = factor(d),
             alpha=factor(d),
               )) + 
      geom_line() + 
  labs(x = the_x_label,
       y = the_y_label,
       title = latex2exp::TeX(long_labels_for_parms[pop_id])) + 
      scale_x_continuous(breaks = c(-3:3)*3 + 1)  + # see above
      the_y_scale +
  theme_classic()+
  theme(plot.title = element_text(hjust=0.5))+
  scale_color_manual(values = colors_for_gg_premium, name = "Premium") +
  scale_linetype_manual(values = c(1, 2), name = "d") +
  scale_linewidth_manual(values = c(1, 0.55), name = 'd')+
  scale_alpha_manual(values=c(0.5,1), name="d")
  }) %>% ggpubr::ggarrange(plotlist = .,
                           nrow = 1, ncol=3,
                           widths = 15, heights = 1,
                           common.legend = T,
                           legend = 'right'))

ggsave(filename = "figs/graph_theo_expected_prem4.pdf",
       plot = to_save_theo_expected_prem4,
       height = 2.75, #2.75,
       width = 8,
       units = "in",
       device = "pdf", dpi = 500)

```

```{r graphlively5, fig.height=4, fig.width=10, echo=FALSE}
(to_save_theo_expected_prem5_temp <- names(parms)[names(parms) %in% c("original", "neutral", "noDtoA")] %>% 
  lapply(function(pop_name){
    
    the_corr_grid <- the_corr_grids[[pop_name]]
    
    
    premDat <- short_grid %>% 
      mutate(x = round(x, 4), 
             best = sapply(1:nrow(short_grid), function(i){
        BEfun(pop_name,
              x=short_grid[i, 'x'],
              d=short_grid[i, 'd'],
                a=1)}),
        un = sapply(1:nrow(short_grid), function(i){
        un_fun_market(pop_name,
                      x=short_grid[i, 'x'],
                 d=short_grid[i, 'd'])}),
        aw = sapply(1:nrow(short_grid), function(i){
        aw_fun_market(pop_name,
                      x=short_grid[i, 'x'],
                      d=short_grid[i, 'd'])})) %>% 
      left_join(., the_corr_grid %>% 
      filter(a == 2) %>% 
      dplyr::select(x, d, mark_exp_corr, corr_ptf) %>% 
        mutate(x = round(x, 4)), 
      by = c('x', 'd')) %>% 
      reshape2::melt(measure.vars = c('corr_ptf' , 'mark_exp_corr','best'))%>%
      mutate(diff = abs(d - ExpDgivenX(pop_name, x)))
    
    suppressWarnings(premDat$value[premDat$diff > 0.999] <- NA)
    
    labels_for_the_corrs <- unname(latex2exp::TeX(c('$\\mu^C(x, d)$', '$\\pi_{corrective}(x, d)$', '$\\mu(x, d)$' )
                                                              ))
    
    pop_id <- which(names(sims) == pop_name)
    
    # keep only axis for last plot
    if(which(pop_name == names(sims)) == 1){
      the_y_label <- latex2exp::TeX("Premium")
      the_y_scale <- scale_y_continuous(breaks = c(90, 110, 130)) 
      the_x_label <- latex2exp::TeX("x")
      } else { 
      the_y_label <- NULL
      the_y_scale <- scale_y_continuous(breaks = c(90, 110, 130)) 
      the_x_label <- latex2exp::TeX("x")
    }
      
      
    premDat %>% 
      ggplot(aes(x = x, y = value,
               col = factor(d),
               lty = variable,
             linewidth = variable,
             alpha=variable,
               )) + 
      geom_line() + 
  labs(x = the_x_label,
       y = the_y_label,
       title = latex2exp::TeX(long_labels_for_parms[pop_id])) + 
      scale_x_continuous(breaks = c(-3:3)*3 + 1)  + # see above
      the_y_scale +
  theme_classic()+
  theme(plot.title = element_text(hjust=0.5))+
  scale_color_manual(values = setNames(colors_for_gg_D, nm = c('0', '1')), name = "d") +
  scale_linetype_manual(values = c('solid', '93', '11'), name = "Premium", labels = labels_for_the_corrs) +
  scale_linewidth_manual(values = c(1.2,  0.65, 0.50), name = 'Premium', labels =labels_for_the_corrs)+
  scale_alpha_manual(values=c(0.25, 0.65, 0.8), name="Premium", labels =labels_for_the_corrs)
  }))

to_save_theo_expected_prem5 <- to_save_theo_expected_prem5_temp %>% ggpubr::ggarrange(plotlist = .,
                           nrow = 1, ncol=3,
                           widths = 15, heights = 1,
                           common.legend = T,
                           legend = 'right')

ggsave(filename = "figs/graph_theo_expected_prem5.pdf",
       plot = to_save_theo_expected_prem5,
       height = 2.75, #2.75,
       width = 8,
       units = "in",
       device = "pdf", dpi = 500)

```


```{r}

library(gtable)
library(grid)

for (i in 1:3) {
  g <- (to_save_theo_corr_prem_temp[[1]] + guides(linewidth = 'none', alpha = 'none', linetype = 'none') + theme(legend.position = 'right')) %>% 
                      ggplotGrob(.)
# Extract all guide-boxes
legend_boxes <- g$grobs[sapply(g$grobs, function(x) x$name) == "guide-box"]

legend <- ggplot() + 
    theme_void() +
    annotation_custom(legend_boxes[[1]])

ggpubr::ggarrange(plotlist = list(to_save_theo_corr_prem_temp[[i]]+
  theme(legend.position = "bottom", legend.direction = "vertical") + labs(title = '')+ 
     guides(color = 'none') + 
    ylab(latex2exp::TeX('$\\mu^C(x, d, A)$')),
  
                                  to_save_theo_corr_prem_marketprop_temp[[i]]+
  theme(legend.position = "bottom", legend.direction = "vertical")+ labs(title = '')+ 
     guides(color = 'none') + 
    ylab(latex2exp::TeX('$\\mu^{C*}_{A}(x, d)$')),
  
                                  to_save_theo_expected_prem5_temp[[i]]+
  theme(legend.position = "bottom", legend.direction = "vertical")+ labs(title = '') + 
     guides(color = 'none')+ 
    ylab(latex2exp::TeX('$Premium$')),
  legend),
                  ncol = 4, widths = c(3, 3, 3, 1)) %>% 
  ggsave(filename = paste0("figs/graph_theo_corr_vertical_", i, ".pdf"),
       plot = .,
       height = 3.75, #2.75,
       width = 8,
       units = "in",
       device = "pdf", dpi = 500)
}



```

Scenario A only for the third panel of the graphical abstract

```{r graphlivelyScA, fig.height=4, fig.width=10, echo=FALSE}

pop_name <- names(parms)[1]


    
    short_grid <- grid_to_test2 %>% 
      filter(a == 1)

    
    premDat <- short_grid %>% 
      mutate(x = round(x, 4), 
             best = sapply(1:nrow(short_grid), function(i){
        BEfun(pop_name,
              x=short_grid[i, 'x'],
              d=short_grid[i, 'd'],
                a=1)}),
        aw = sapply(1:nrow(short_grid), function(i){
        aw_fun_market(pop_name,
                      x=short_grid[i, 'x'],
                      d=short_grid[i, 'd'])})) %>% 
      reshape2::melt(measure.vars = c('best', 'aw'))%>%
      mutate(diff = abs(d - ExpDgivenX(pop_name, x)))
    
    suppressWarnings(premDat$value[premDat$variable == 'best'][premDat$diff > 0.999] <- NA)
    suppressWarnings(premDat$value[premDat$variable == 'aw'][premDat$diff > 0.999] <- NA)
    
    pop_id <- which(names(sims) == pop_name)
    
    # keep only axis for last plot
    if(which(pop_name == names(sims)) == 1){
      the_y_label <- latex2exp::TeX("Premium")
      the_y_scale <- scale_y_continuous(breaks = c(90, 110, 130)) 
      the_x_label <- latex2exp::TeX("x")
      } else { 
      the_y_label <- NULL
      the_y_scale <- scale_y_continuous(breaks = c(90, 110, 130)) 
      the_x_label <- latex2exp::TeX("x")
    }
      
      
(to_save_theo_expected_prem_ScA <-     premDat %>% 
      ggplot(aes(x = x, y = value,
               col = variable,
               lty = factor(d),
               linewidth=variable
               )) + 
      geom_line() + 
  labs(x = the_x_label,
       y = the_y_label) + 
      scale_x_continuous(breaks = c(-3:4)*3 + 1)  + # see above
      scale_y_continuous(breaks = c(80, 100,120, 140))  +
  theme_classic()+
  scale_color_manual(values = colors_for_gg_premium, name = "Premium", labels=c("E(Y|x,d)","Aware")) +
  scale_linetype_manual(values = c(1, 4), name = "", 
                        labels=c("d=0","d=1")) +
  scale_linewidth_manual(values = c(1.1,1), name = 'Premium',
                         labels=c("E(Y|x,d)","Aware"))+
  theme(panel.background=element_rect(fill="transparent"),
        plot.background = element_rect(fill='transparent', color=NA),
        legend.background = element_rect(fill='transparent'),
        legend.position=c(1,0.35),
  plot.margin=margin(5.5,30,5.5,5.5)))

ggsave(filename = "figs/graph_theo_expected_prem_ScA.pdf",
       plot = to_save_theo_expected_prem_ScA,
       height = 2.9,
       width = 3,
       units = "in",
       device = "pdf", dpi = 500)



```

## Graph for presentations

This is the code for the version of the graph we use for presentations. A ARRANGER CAR NE ROULE PAS MAINTENANT.

```{r graphforpres, echo=FALSE}
the_bias_colors <- c('black', '#9966CC', "#AEAEAE", '#F7798D')
the_bias_labels <- unname(TeX(c("$\\mu^{P}(x, d)$   ", "$\\mu^{U}(x)$", "$\\mu^{C}(x)$", '$\\mu^{M, C}(x, d)$')))
the_bias_premiums <- c('best', 'un', 'aw_market', 'aw_by_ins')
    

# to_save_theo_aw_by_pop <- seq_along(the_bias_colors) %>% 
#   lapply(function(the_number){
#     
#     pop_name = 'original'
#     
#     short_grid <- grid_to_test2 %>% 
#       filter(a == 'A=1')
#     
#     
#     premDat <- short_grid %>% 
#       mutate(best = sapply(1:nrow(short_grid), function(i){
#         best_fun(short_grid[i, 'x'],
#                  short_grid[i, 'd'],
#                  1,
#                  parms[[pop_name]])}),
#         aw_market = sapply(1:nrow(short_grid), function(i){
#         aw_fun(x = short_grid[i, 'x'],
#               d = short_grid[i, 'd'],
#               a = 'market', 
#               param = parms[[pop_name]])}),
#         un = sapply(1:nrow(short_grid), function(i){
#         un_fun(x = short_grid[i, 'x'],
#               d = short_grid[i, 'd'],
#               a = 'market',
#                  parms[[pop_name]])}),
#               aw_market = sapply(1:nrow(short_grid), function(i){
#         aw_fun(x = short_grid[i, 'x'],
#               d = short_grid[i, 'd'],
#               a = 'market', 
#               param = parms[[pop_name]])}),
#             aw_by_ins = sapply(1:nrow(short_grid), function(i){
#         aw_fun_market(short_grid[i, 'x'],
#                  short_grid[i, 'd'],
#                  parms[[pop_name]])})) %>% 
#       reshape2::melt(measure.vars = the_bias_premiums[seq(the_number)]) %>% 
#       mutate(diff = abs(d - ExpDgivenX(pop_name, x)))
#     
#     suppressWarnings(premDat$value[premDat$variable == 'best'][premDat$diff > 0.999] <- NA)
#     
#     pop_id <- which(names(sims) == pop_name)
#     
#     # keep only axis for last plot
#     if(which(pop_name == names(sims)) == 1){
#       the_y_label <- latex2exp::TeX("Valeur de la prime")
#       the_y_scale <- scale_y_continuous()
#       the_x_label <- latex2exp::TeX("x")
#       } else { 
#       the_y_label <- NULL
#       the_y_scale <- scale_y_continuous(labels = NULL)
#       the_x_label <- latex2exp::TeX("x")
#     }
#       
#     to_save_theo_aw_by_pop <- premDat %>% 
#       filter(x > -9) %>% 
#       ggplot(aes(x = x, y = value,
#                col = variable,
#                lty = factor(d),
#              linewidth = factor(d),
#                )) + 
#       geom_line(alpha = 0.65) + 
#   labs(x = the_x_label,
#        y = the_y_label
#        # ,title = latex2exp::TeX(long_labels_for_parms[pop_id])
#        ) + 
#       scale_x_continuous(breaks = c(-3:3)*3 + 1)  + # see above
#       the_y_scale +
#   theme_classic()+
#   coord_fixed(ratio = 1/3.8) + 
#   theme(plot.title = element_text(hjust=0.5),
#         plot.margin = unit(c(0.0, 0.0, 0.0, 0.0), "in"))+
#   scale_color_manual(values = the_bias_colors, name = "Prime",
#                      labels = the_bias_labels) +
#   scale_linetype_manual(values = c(1, 2), name = "d") +
#   scale_linewidth_manual(values = c(1, 0.55), name = 'd') +
#       theme(legend.position = 'bottom', legend.box="horizontal",
#             legend.direction = 'vertical')+
#   guides(
#     col = guide_legend(nrow = 4, order = 1),  # Control number of columns for consistency
#     lty = guide_legend(nrow = 4, order = 2),
#     linewidth = guide_legend(nrow = 4, order = 2)
#   )
#     
#     
#   ggsave(filename = paste0("figs/graph_theo_aw_by_pop", the_number, "_base.pdf"),
#        plot = to_save_theo_aw_by_pop,
#        height = 4,
#        width = 2.8,
#        units = "in",
#        device = "pdf", dpi = 500)
#   }) 

```


# The models

In this section, we estimate the models based on the complete market and on the separate Insurer portfolios. 

## Best-estimate

```{r bemodel, cache=TRUE}
source('___lgb_best_estimate.R')

## clean the pred repo
unlink(file.path('preds', "*_best_estimate.json"))
best_lgb <- setNames(nm = names(sims)) %>% lapply(the_best_estimate_lightgbm_fun)

```


Fit LightGBM BE model for each of the two portfolios: they should both be unbiased. From the graph, it seems to work just fine.

```{r bemodelptf, cache=TRUE, fig.width=10, fig.height=8}
best_lgb_A1 <- setNames(nm = names(sims)) %>% lapply(the_best_estimate_lightgbm_fun, selectA=1)
best_lgb_A0 <- setNames(nm = names(sims)) %>% lapply(the_best_estimate_lightgbm_fun, selectA=0)

par(mfrow=c(2,3))
lapply(names(sims), function(pop_name){
plot(best_lgb[[pop_name]]$preds$valid[valid[[pop_name]]$A==0], best_lgb_A0[[pop_name]]$preds$valid, col=colors_for_gg_A[1], xlab="Market prediction", ylab="Portfolio prediction", ylim=c(80,140), xlim=c(80,140), main=long_labels_for_parms[pop_name])
points(best_lgb[[pop_name]]$preds$valid[valid[[pop_name]]$A==1], best_lgb_A1[[pop_name]]$preds$valid, col=colors_for_gg_A[2])
})
```


## Marginal model for D

```{r margd}
(marg_dist <- sims %>% lapply(function(data){
  data$D %>% table %>%  prop.table
}))

(marg_dist_A0 <- sims %>% lapply(function(data){
  data$D[which(data$A==0)] %>% table %>%  prop.table
}))

(marg_dist_A1 <- sims %>% lapply(function(data){
  data$D[which(data$A==1)]  %>% table %>%  prop.table
}))
```


## Conditional dist of D|X

```{r pdxmodel, cache=TRUE}
source('___lgb_pdx_estimate.R') 

## clean the preds repo
unlink(file.path('preds', "*_pdx.json"))
pdx_lgb <- setNames(nm = names(sims)) %>% lapply(the_pdx_lightgbm_fun)
```

Run pdx for each of the two portfolios: they will differ.

```{r pdxmodelptf, cache=TRUE, fig.width=10, fig.height=8}
pdx_lgb_A1 <- setNames(nm = names(sims)) %>% lapply(the_pdx_lightgbm_fun, selectA=1)
pdx_lgb_A0 <- setNames(nm = names(sims)) %>% lapply(the_pdx_lightgbm_fun, selectA=0)


par(mfrow=c(2,3))
lapply(names(sims), function(pop_name){
plot(pdx_lgb[[pop_name]]$preds$valid[valid[[pop_name]]$A==0], pdx_lgb_A0[[pop_name]]$preds$valid[valid[[pop_name]]$A==0], col=colors_for_gg_A[1], xlab="Market pdx", ylab="Portfolio pdx", ylim=c(0,1), xlim=c(0,1), main=long_labels_for_parms[pop_name])
points(pdx_lgb[[pop_name]]$preds$valid[valid[[pop_name]]$A==1], pdx_lgb_A1[[pop_name]]$preds$valid[valid[[pop_name]]$A==1], col=colors_for_gg_A[2])
})
```


## Unaware premium

```{r unmodel, cache=TRUE}
source('___lgb_unaware.R') 

## clean the preds repo
unlink(file.path('preds', "*_unaware.json"))
unaware_lgb <- setNames(nm = names(sims)) %>% lapply(the_unaware_lightgbm_fun)

```

Run unaware for each of the two portfolios: they will differ.

```{r unmodelptf, cache=TRUE}
unaware_lgb_A1 <- setNames(nm = names(sims)) %>% lapply(the_unaware_lightgbm_fun, selectA=1)
unaware_lgb_A0 <- setNames(nm = names(sims)) %>% lapply(the_unaware_lightgbm_fun, selectA=0)

par(mfrow=c(2,3))
lapply(names(sims), function(pop_name){
plot(unaware_lgb[[pop_name]]$preds$valid[valid[[pop_name]]$A==0], unaware_lgb_A0[[pop_name]]$preds$valid, col=colors_for_gg_A[1], xlab="Market prediction", ylab="Portfolio prediction", ylim=c(80,140), xlim=c(80,140), main=long_labels_for_parms[pop_name])
points(unaware_lgb[[pop_name]]$preds$valid[valid[[pop_name]]$A==1], unaware_lgb_A1[[pop_name]]$preds$valid, col=colors_for_gg_A[2])
})
```


## The OT mapping

Python was set up earlier in the document. 

```{r OTmap}

source_python("___opt_transp.py")

## now, the folder 'transported' exist, with one epsilon_y file per scenario
```


## (Temporary cheat) mapping to corrective

I want a mapping, from (SB, D)  to SC. Optimal transport (previous section) is supposed to be okay, but I ain't convinced yet. 

```{r lgbmapping, cache=TRUE}
source('___lgb_mapping_to_corr.R')

corr_mapping_lgb <- setNames(nm = names(sims)) %>%
 lapply(the_mapping_to_corr_lightgbm_fun, selectA=0:1)

corr_mapping_lgb_A0 <- setNames(nm = names(sims)) %>%
 lapply(the_mapping_to_corr_lightgbm_fun, selectA=0)

corr_mapping_lgb_A1 <- setNames(nm = names(sims)) %>%
 lapply(the_mapping_to_corr_lightgbm_fun, selectA=1)

```


# The families of premiums

We need a few ggplot2 tools in `___function.R`.

We will store the five families of premium, first we compute them on the entire market.

```{r premcalc}
levels_for_scores <- c("SB", "SU", "SA", "SH", "SC")
labels_for_scores <- c("$S^B(X, D)$","$S^U(X)$", "$S^A(X)$", "$S^H(X)$", "$S^C(\\epsilon_X)$")

scores <- setNames(nm = names(sims)) %>% lapply(function(name){
  list("SB" = function(x, d){
    
    ## simple call of the best estimate model
    best_lgb[[name]]$pred_fun(data.frame(X = x, D = d))
  }, "SU" = function(x, d=NULL){
    
    ## simple call of the unaware model
    unaware_lgb[[name]]$pred_fun(data.frame(X = x))
  }, "SA" = function(x, d = NULL){
    
    ## SA = E(SB) unconditional
    sapply(0:1, function(d){best_lgb[[name]]$pred_fun(data.frame(X = x, D = d))*
       marg_dist[[name]][d + 1]}) %>% apply(1, sum)
   }, "SH" = function(x, d = NULL){

    ## Here we cheated by using our mapping of SC
    ## explicit inference of SC : SH = E(SC|X)
    tab_corr <- sapply(0:1, function(dl){
      sb <- best_lgb[[name]]$pred_fun(data.frame(X = x, D = dl))
      corr_mapping_lgb[[name]](data.frame(SB = sb, D = dl))
      })
    tab_pdx <- sapply(0:1, function(dl){
      pdx_lgb[[name]]$pred_fun(data.frame(X = x, D = dl))
      })

    (tab_corr * tab_pdx) %>% apply(1, sum)
  }, "SC" = function(x, d){

    ## SC = T^{d \to \star}(SB(x, d))
    sb <- best_lgb[[name]]$pred_fun(data.frame(X = x, D = d))
    corr_mapping_lgb[[name]](data.frame(SB = sb, D = d))
  }
    )
})

```

We also store the versions by portfolio:

```{r premcalcptf}
levels_for_scores_A <- c("SB", "SU", "SA", "SA.pp", "SH", "SC")
labels_for_scores_A <- c("$S^B(X, D)$","$S^U(X)$", "$S^A(X)$","$S^A_p(X)$", "$S^H(X)$", "$S^C(\\epsilon_X)$")

scores_A0 <- setNames(nm = names(sims)) %>% lapply(function(name){
  list("SB" = function(x, d){
    
    ## simple call of the best estimate model
    best_lgb_A0[[name]]$pred_fun(data.frame(X = x, D = d))
  }, "SU" = function(x, d=NULL){
    
    ## simple call of the unaware model
    unaware_lgb_A0[[name]]$pred_fun(data.frame(X = x))
  }, "SA" = function(x, d = NULL){
    
    ## SA = E(SB) unconditional
    sapply(0:1, function(d){best_lgb_A0[[name]]$pred_fun(data.frame(X = x, D = d))*
       marg_dist_A0[[name]][d + 1]}) %>% apply(1, sum)
  },"SA.pp" = function(x, d = NULL){
    
    ## SA = E(SB) unconditional
    sapply(0:1, function(d){best_lgb_A0[[name]]$pred_fun(data.frame(X = x, D = d))*
       marg_dist[[name]][d + 1]}) %>% apply(1, sum)
  }, "SH" = function(x, d = NULL){
    
    ## Here we cheated by using our mapping of SC
    ## explicit inference of SC : SH = E(SC|X)
    tab_corr <- sapply(0:1, function(dl){
      sb <- best_lgb_A0[[name]]$pred_fun(data.frame(X = x, D = dl))
      corr_mapping_lgb_A0[[name]](data.frame(SB = sb, D = dl))
      })
    tab_pdx <- sapply(0:1, function(dl){
      pdx_lgb_A0[[name]]$pred_fun(data.frame(X = x, D = dl))
      })

    (tab_corr * tab_pdx) %>% apply(1, sum)
  }, "SC" = function(x, d){

    ## SC = T^{d \to \star}(SB(x, d))
    sb <- best_lgb_A0[[name]]$pred_fun(data.frame(X = x, D = d))
    corr_mapping_lgb_A0[[name]](data.frame(SB = sb, D = d))
  }
  )
})

scores_A1 <- setNames(nm = names(sims)) %>% lapply(function(name){
  list("SB" = function(x, d){
    
    ## simple call of the best estimate model
    best_lgb_A1[[name]]$pred_fun(data.frame(X = x, D = d))
  }, "SU" = function(x, d=NULL){
    
    ## simple call of the unaware model
    unaware_lgb_A1[[name]]$pred_fun(data.frame(X = x))
  }, "SA" = function(x, d = NULL){
    
    ## SA = E(SB) unconditional
    sapply(0:1, function(d){best_lgb_A1[[name]]$pred_fun(data.frame(X = x, D = d))*
       marg_dist_A1[[name]][d + 1]}) %>% apply(1, sum)
  },"SA.pp" = function(x, d = NULL){
    
    ## SA = E(SB) unconditional
    sapply(0:1, function(d){best_lgb_A1[[name]]$pred_fun(data.frame(X = x, D = d))*
       marg_dist[[name]][d + 1]}) %>% apply(1, sum)
  }, "SH" = function(x, d = NULL){
    
  # Here we cheated by using our mapping of SC
  # explicit inference of SC : SH = E(SC|X)
    tab_corr <- sapply(0:1, function(dl){
      sb <- best_lgb_A1[[name]]$pred_fun(data.frame(X = x, D = dl))
      corr_mapping_lgb_A1[[name]](data.frame(SB = sb, D = dl))
      })
    tab_pdx <- sapply(0:1, function(dl){
      pdx_lgb_A1[[name]]$pred_fun(data.frame(X = x, D = dl))
      })

    (tab_corr * tab_pdx) %>% apply(1, sum)
  }, "SC" = function(x, d){

    ## SC = T^{d \to \star}(SB(x, d))
    sb <- best_lgb_A1[[name]]$pred_fun(data.frame(X = x, D = d))
    corr_mapping_lgb_A1[[name]](data.frame(SB = sb, D = d))
  }
  )
})
```


Now let's try. We compute and store each premium on all scenario over a grid of (x,d) values for the plots.

```{r df_to_g}
grid_to_test <- expand.grid(x = seq(-10, 11, by = 0.05),
                            d = c(0, 1))

df_to_g <- setNames(nm = names(sims)) %>% lapply(function(name){
  data.frame(grid_to_test, 
           setNames(nm = levels_for_scores) %>% 
  sapply(function(s){
    scores[[name]][[s]](x = grid_to_test$x, d = grid_to_test$d)
  }))
})

df_to_g_A0 <- setNames(nm = names(sims)) %>% lapply(function(name){
  data.frame(grid_to_test, 
           setNames(nm = levels_for_scores_A) %>% 
  sapply(function(s){
    scores_A0[[name]][[s]](x = grid_to_test$x, d = grid_to_test$d)
  }))
})

df_to_g_A1 <- setNames(nm = names(sims)) %>% lapply(function(name){
  data.frame(grid_to_test, 
           setNames(nm = levels_for_scores_A) %>% 
  sapply(function(s){
    scores_A1[[name]][[s]](x = grid_to_test$x, d = grid_to_test$d)
  }))
})
```

## Best-estimate versus X

```{r BEvsX, fig.width=12, echo=FALSE}

(to_save_BE_vsX <- names(df_to_g_A1)[1:3] %>% 
  lapply(function(name){
    ## The premiums
    premDat <- rbind(df_to_g[[name]][,c(1,2,3)],df_to_g_A1[[name]][,c(1,2,3)],df_to_g_A0[[name]][,c(1,2,3)]) %>% mutate(Portfolio=rep(c("market","A=1","A=0"), each=dim(df_to_g_A0$original)[1]))
    
    ## the colors
    premDat$Portfolio <- factor(premDat$Portfolio,
                                levels = names(colors_for_gg_market))
    
    ## Make sure to keep the right order
    cols <- levels(premDat$Portfolio) %>% sapply(function(lvl){
      colors_for_gg_market[which(lvl == names(colors_for_gg_market))] %>% unname
    })
    
    pop_id <- which(names(df_to_g_A1) == name)
    
    # keep only axis for last plot
    if(which(name == names(df_to_g_A1)) == 1){
      the_y_label <- latex2exp::TeX("Best-estimate premium")
      the_x_label <- latex2exp::TeX("$x$")
    } else if(which(name == names(df_to_g_A1)) == 4){ # If it's on the left, apply correct xlabels
      the_y_label <- latex2exp::TeX("Best-estimate premium")
      the_x_label <- latex2exp::TeX("$x$")
    } else if(which(name == names(df_to_g_A1)) %in% c(5, 6)){ # If it's on the left, apply correct xlabels
      the_y_label <- NULL
      the_x_label <- latex2exp::TeX("$x$")
    } else { 
      the_y_label <- NULL
      the_x_label <- latex2exp::TeX("$x$")
    }
    
    ## lets graph
    premDat %>% 
      mutate(the_population = name) %>% 
  filter(x >= -9, x <= 10) %>% 
  ggplot(aes(x = x, y = SB,
             col = Portfolio,
             fill = Portfolio,
             lty = Portfolio,
             linewidth = factor(d))) +
  geom_line(alpha = 0.75) +
  scale_color_manual(values = cols, name = "A") +
  scale_fill_manual(values = cols, name = "A") +
  scale_linetype_manual(values = c(1, 3, 2), name = "A") +
  scale_linewidth_manual(values = c(1.7, 0.85, 1), name = 'd') + 
  scale_alpha_manual(values = c(1, 0.3), guide = "none") +
  labs(x = the_x_label,
       y = the_y_label,
       title = latex2exp::TeX(long_labels_for_parms[pop_id])) +
       # title = latex2exp::TeX("$D \\nrightarrow X $")) + 
  scale_x_continuous(breaks = c(-3:3)*4 )  + # see above
  scale_y_continuous(breaks = seq(70, 150, by=20), limits=c(70,150)) + 
  theme_classic() + 
#  the_y_scale +
  guides(color = guide_legend(override.aes = list(linewidth = 1.5)),  # Adjust linewidth for 'Pop.' legend
         fill = guide_legend(override.aes = list(linewidth = 1.5)),   # Ensure consistency across color and fill
         linetype = guide_legend(override.aes = list(linewidth = 1.5))) +  # Adjust linetype legend if needed
  
  theme(plot.title = element_text(hjust=0.5))
  }) %>% ggpubr::ggarrange(plotlist = .,
                           nrow = 1, ncol=3,
                           widths = 12, heights = 1,
                           common.legend = T,
                           legend = 'right'))

ggsave(filename = "figs/graph_BE_vsX.pdf",
       plot = to_save_BE_vsX,
       height = 3,
       width = 9,
       units = "in",
       device = "pdf", dpi = 500)
```

## Unaware vs X

```{r UnawarevsX, fig.width=12, echo=FALSE}
(to_save_unaware_vsX <- names(df_to_g_A1)[1:3] %>% lapply(function(pop_name){
graph_to_return <- rbind(df_to_g[[pop_name]][,c(1,2,4)],df_to_g_A1[[pop_name]][,c(1,2,4)],df_to_g_A0[[pop_name]][,c(1,2,4)]) %>% mutate(Portfolio=rep(c("market","A=1","A=0"), each=dim(df_to_g_A0$original)[1]))

## the colors
    graph_to_return$Portfolio <- factor(graph_to_return$Portfolio,
                                levels = names(colors_for_gg_market))
    
    ## Make sure to keep the right order
    cols <- levels(graph_to_return$Portfolio) %>% sapply(function(lvl){
      colors_for_gg_market[which(lvl == names(colors_for_gg_market))] %>% unname
    })
    
    pop_id <- which(names(df_to_g_A1) == pop_name)
    
    # keep only axis for last plot
    if(which(pop_name == names(df_to_g_A1)) == 1){
      the_y_label <- latex2exp::TeX("Unaware premium")
      the_x_label <- latex2exp::TeX("$x$")
    } else if(which(pop_name == names(df_to_g_A1)) == 4){ # If it's on the left, apply correct xlabels
      the_y_label <- latex2exp::TeX("Unaware premium")
      the_x_label <- latex2exp::TeX("$x$")
    } else if(which(pop_name == names(df_to_g_A1)) %in% c(5, 6)){ # If it's on the left, apply correct xlabels
      the_y_label <- NULL
      the_x_label <- latex2exp::TeX("$x$")
    } else { 
      the_y_label <- NULL
      the_x_label <- latex2exp::TeX("$x$")
    }
    
    
graph_to_return %>%
  filter(x >= -9, x <= 10) %>% 
  ggplot(aes(x=x, y=SU,
             col=Portfolio,
             fill=Portfolio,
             linetype =Portfolio))+
  geom_line(alpha = 0.75, linewidth = 1) +
  scale_color_manual(values = cols, name = "A") +
  scale_fill_manual(values = cols, name = "A") +
  scale_linetype_manual(values = c(1, 3, 2), name = "A") +
labs(x = the_x_label,
       y = the_y_label,
       title = latex2exp::TeX(long_labels_for_parms[pop_name]))+
    scale_x_continuous(breaks = c(-3:3)*4 )  +
    scale_y_continuous(breaks = seq(70, 150, by=20), limits=c(70,150)) +
    theme_classic()+
  theme(plot.title = element_text(hjust=0.5))
})%>% ggpubr::ggarrange(plotlist = .,
                           nrow = 1, ncol=3,
                           widths = 15, heights = 1,
                           common.legend = T,
                           legend = 'right'))

ggsave(filename = "figs/graph_unaware_vsX.pdf",
       plot = to_save_unaware_vsX,
       height = 3,
       width = 9,
       units = "in",
       device = "pdf", dpi = 500)
```


## Aware vs X

The first graph is the aware by portfolio. The second graph is the "unbiased" version of the aware premium, computed with the marginal distribution of D in the population.

```{r AwarevsX, fig.width=12, echo=FALSE}

(to_save_Aware_vsX <- names(df_to_g_A1)[1:3] %>% lapply(function(pop_name){
graph_to_return <- rbind(df_to_g[[pop_name]][,c(1,2,5)],df_to_g_A1[[pop_name]][,c(1,2,5)],df_to_g_A0[[pop_name]][,c(1,2,5)]) %>% mutate(Portfolio=rep(c("market","A=1","A=0"), each=dim(df_to_g_A0$original)[1])) 

## the colors
    graph_to_return$Portfolio <- factor(graph_to_return$Portfolio,
                                levels = names(colors_for_gg_market))
    
    ## Make sure to keep the right order
    cols <- levels(graph_to_return$Portfolio) %>% sapply(function(lvl){
      colors_for_gg_market[which(lvl == names(colors_for_gg_market))] %>% unname
    })
    
    pop_id <- which(names(df_to_g_A1) == pop_name)
    
    # keep only axis for last plot
    if(which(pop_name == names(df_to_g_A1)) == 1){
      the_y_label <- latex2exp::TeX("Aware premium")
      the_x_label <- latex2exp::TeX("$x$")
    } else if(which(pop_name == names(df_to_g_A1)) == 4){ # If it's on the left, apply correct xlabels
      the_y_label <- latex2exp::TeX("Aware premium")
      the_x_label <- latex2exp::TeX("$x$")
    } else if(which(pop_name == names(df_to_g_A1)) %in% c(5, 6)){ # If it's on the left, apply correct xlabels
      the_y_label <- NULL
      the_x_label <- latex2exp::TeX("$x$")
    } else { 
      the_y_label <- NULL
      the_x_label <- latex2exp::TeX("$x$")
    }
    
  graph_to_return %>%
  filter(x >= -9, x <= 10) %>% 
  ggplot(aes(x=x, y=SA, 
             col=Portfolio,
             fill=Portfolio,
             linetype =Portfolio))+
  geom_line(alpha = 0.75, linewidth = 1) +
  scale_color_manual(values = cols, name = "A") +
  scale_fill_manual(values = cols, name = "A") +
  scale_linetype_manual(values = c(1, 3, 2), name = "A") +
labs(x = the_x_label,
       y = the_y_label,
       title = latex2exp::TeX(long_labels_for_parms[pop_name]))+
    scale_x_continuous(breaks = c(-3:3)*4 )  +
    scale_y_continuous(breaks = seq(70, 150, by=20), limits=c(70,150)) +
    theme_classic()+
  theme(plot.title = element_text(hjust=0.5))
  })%>% ggpubr::ggarrange(plotlist = .,
                           nrow = 1, ncol=3,
                           widths = 12, heights = 1,
                           common.legend = T,
                           legend = 'right'))

ggsave(filename = "figs/graph_Aware_vsX.pdf",
       plot = to_save_Aware_vsX,
       height = 3,
       width = 9,
       units = "in",
       device = "pdf", dpi = 500)

(to_save_Awarepop_vsX <- names(df_to_g_A1)[1:3] %>% lapply(function(pop_name){
graph_to_return <- df_to_g[[pop_name]][,c(1,2,5)]%>% rename(SA.pp = SA) %>%
  rbind(df_to_g_A1[[pop_name]][,c(1,2,6)],df_to_g_A0[[pop_name]][,c(1,2,6)])%>% 
  mutate(Portfolio=rep(c("market","A=1","A=0"), each=dim(df_to_g_A0$original)[1])) 

## the colors
    graph_to_return$Portfolio <- factor(graph_to_return$Portfolio,
                                levels = names(colors_for_gg_market))
    
    ## Make sure to keep the right order
    cols <- levels(graph_to_return$Portfolio) %>% sapply(function(lvl){
      colors_for_gg_market[which(lvl == names(colors_for_gg_market))] %>% unname
    })
    
    pop_id <- which(names(df_to_g_A1) == pop_name)
    
    # keep only axis for last plot
    if(which(pop_name == names(df_to_g_A1)) == 1){
      the_y_label <- latex2exp::TeX("Aware premium (market prop)")
      the_x_label <- latex2exp::TeX("$x$")
    } else if(which(pop_name == names(df_to_g_A1)) == 4){ # If it's on the left, apply correct xlabels
      the_y_label <- latex2exp::TeX("Aware premium (market prop)")
      the_x_label <- latex2exp::TeX("$x$")
    } else if(which(pop_name == names(df_to_g_A1)) %in% c(5, 6)){ # If it's on the left, apply correct xlabels
      the_y_label <- NULL
      the_x_label <- latex2exp::TeX("$x$")
    } else { 
      the_y_label <- NULL
      the_x_label <- latex2exp::TeX("$x$")
    }

graph_to_return %>%
  filter(x >= -9, x <= 10) %>% 
  ggplot(aes(x=x, y=SA.pp, 
             col=Portfolio,
             fill=Portfolio,
             linetype =Portfolio))+
  geom_line(alpha = 0.75, linewidth = 1) +
  scale_color_manual(values = cols, name = "A") +
  scale_fill_manual(values = cols, name = "A") +
  scale_linetype_manual(values = c(1, 3, 2), name = "A") +
labs(x = the_x_label,
       y = the_y_label,
       title = latex2exp::TeX(long_labels_for_parms[pop_name]))+
    scale_x_continuous(breaks = c(-3:3)*4 )  +
    scale_y_continuous(breaks = seq(70, 150, by=20), limits=c(70,150)) +
    theme_classic()+
  theme(plot.title = element_text(hjust=0.5))
})%>% ggpubr::ggarrange(plotlist = .,
                           nrow = 1, ncol=3,
                           widths = 15, heights = 1,
                           common.legend = T,
                           legend = 'right'))

ggsave(filename = "figs/graph_AwarePop_vsX.pdf",
       plot = to_save_Awarepop_vsX,
       height = 3,
       width = 9,
       units = "in",
       device = "pdf", dpi = 500)

```


## Corrective

```{r CorrectivevsX, echo=FALSE, fig.width=12}
(to_save_Corrective_vsX <- names(df_to_g_A1)[1:3] %>% lapply(function(pop_name){
graph_to_return <- rbind(df_to_g[[pop_name]][,c(1,2,7)],df_to_g_A1[[pop_name]][,c(1,2,8)],df_to_g_A0[[pop_name]][,c(1,2,8)]) %>% mutate(Portfolio=rep(c("market","A=1","A=0"), each=dim(df_to_g_A0$original)[1])) 
    
## the colors
    graph_to_return$Portfolio <- factor(graph_to_return$Portfolio,
                                levels = names(colors_for_gg_market))
    
    ## Make sure to keep the right order
    cols <- levels(graph_to_return$Portfolio) %>% sapply(function(lvl){
      colors_for_gg_market[which(lvl == names(colors_for_gg_market))] %>% unname
    })
    
    pop_id <- which(names(df_to_g_A1) == pop_name)
    
    # keep only axis for last plot
    if(which(pop_name == names(df_to_g_A1)) == 1){
      the_y_label <- latex2exp::TeX("Corrective premium")
      the_x_label <- latex2exp::TeX("$x$")
    } else if(which(pop_name == names(df_to_g_A1)) == 4){ # If it's on the left, apply correct xlabels
      the_y_label <- latex2exp::TeX("Corrective premium")
      the_x_label <- latex2exp::TeX("$x$")
    } else if(which(pop_name == names(df_to_g_A1)) %in% c(5, 6)){ # If it's on the left, apply correct xlabels
      the_y_label <- NULL
      the_x_label <- latex2exp::TeX("$x$")
    } else { 
      the_y_label <- NULL
      the_x_label <- latex2exp::TeX("$x$")
    }
    
  graph_to_return %>%
  filter(x >= -9, x <= 10) %>% 
 ggplot(aes(x = x, y = SC,
             col = Portfolio,
             fill = Portfolio,
             lty = Portfolio,
             linewidth = factor(d))) +
  geom_line(alpha = 0.75) +
  scale_color_manual(values = cols, name = "A") +
  scale_fill_manual(values = cols, name = "A") +
  scale_linetype_manual(values = c(1, 3, 2), name = "A") +
  scale_linewidth_manual(values = c(1.7, 0.85, 1), name = 'd') + 
  scale_alpha_manual(values = c(1, 0.3), guide = "none") +
  labs(x = the_x_label,
       y = the_y_label,
       title = latex2exp::TeX(long_labels_for_parms[pop_id])) +
       # title = latex2exp::TeX("$D \\nrightarrow X $")) + 
  scale_x_continuous(breaks = c(-3:3)*4 )  + # see above
  scale_y_continuous(breaks = seq(70, 150, by=20), limits=c(70,150)) + 
  theme_classic() + 
#  the_y_scale +
  guides(color = guide_legend(override.aes = list(linewidth = 1.5)),  # Adjust linewidth for 'Pop.' legend
         fill = guide_legend(override.aes = list(linewidth = 1.5)),   # Ensure consistency across color and fill
         linetype = guide_legend(override.aes = list(linewidth = 1.5))) +  # Adjust linetype legend if needed
  
  theme(plot.title = element_text(hjust=0.5))
  })%>% ggpubr::ggarrange(plotlist = .,
                           nrow = 1, ncol=3,
                           widths = 12, heights = 1,
                           common.legend = T,
                           legend = 'right'))

ggsave(filename = "figs/graph_Corrective_vsX.pdf",
       plot = to_save_Corrective_vsX,
       height = 3,
       width = 9,
       units = "in",
       device = "pdf", dpi = 500)
```


## Mean premium paid over market

The theoretical versions of these graphs are easier to grasp, so we might not keep this one?

```{r}
colors_for_gg_premium2 <- c("Best"=colors_for_gg_premium[1],
                           "Unaware"=colors_for_gg_premium[2],
                           "Aware"= colors_for_gg_premium[3])

(to_save_meanprem <- names(df_to_g_A1)[1:3] %>% lapply(function(pop_name){

premB_bycomp <- rep(0, n/10)
premB_bycomp[which(test[[pop_name]]$A==1)] <-  scores_A1[[pop_name]]$SB(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==1)]
premB_bycomp[which(test[[pop_name]]$A==0)] <-  scores_A0[[pop_name]]$SB(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==0)]


premA_bycomp <- rep(0, n/10)
premA_bycomp[which(test[[pop_name]]$A==1)] <-  scores_A1[[pop_name]]$SA(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==1)]
premA_bycomp[which(test[[pop_name]]$A==0)] <-  scores_A0[[pop_name]]$SA(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==0)]

premU_bycomp <- rep(0, n/10)
premU_bycomp[which(test[[pop_name]]$A==1)] <-  scores_A1[[pop_name]]$SU(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==1)]
premU_bycomp[which(test[[pop_name]]$A==0)] <-  scores_A0[[pop_name]]$SU(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==0)]

premC_bycomp <- rep(0, n/10)
premC_bycomp[which(test[[pop_name]]$A==1)] <-  scores_A1[[pop_name]]$SC(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==1)]
premC_bycomp[which(test[[pop_name]]$A==0)] <-  scores_A0[[pop_name]]$SC(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==0)]

xseq <- seq(-10.5,12, by=0.5)
Xdiscretized <- cut(test[[pop_name]]$X, xseq)
midpoint.vec <- xseq[-length(xseq)] + diff(xseq)/2
names(midpoint.vec) <- levels(Xdiscretized)
Xmid <- midpoint.vec[Xdiscretized]
  
  pop_id <- which(names(df_to_g_A1) == pop_name)
    
    # keep only axis for last plot
    if(which(pop_name == names(df_to_g_A1)) %in% c(1,4)){
      the_y_label <- latex2exp::TeX("Premium")
      the_y_scale <- scale_y_continuous()
      the_x_label <- latex2exp::TeX("x")
      } else { 
      the_y_label <- NULL
      the_y_scale <- scale_y_continuous(labels = NULL)
      the_x_label <- latex2exp::TeX("x")
      }
  
aggregate(cbind(Best, Unaware, Aware)~Xdisc+D, FUN=mean,
          data=test[[pop_name]]%>% mutate(Aware = premA_bycomp, 
                                          Best = premB_bycomp, 
                                          Unaware = premU_bycomp,
                                          Corrective = premC_bycomp,
                                          Xdisc = Xmid))%>%
  reshape2::melt(measure.vars = c("Best", "Unaware", "Aware"))%>%
    filter(Xdisc >= -8, Xdisc <= 10) %>%
ggplot(aes(x=Xdisc, y=value,
           col=variable,
           lty=factor(D),
           alpha=factor(D),
           linewidth=factor(D)))+
  geom_line(alpha=0.75)+ 
  labs(x = the_x_label,
       y = the_y_label,
       title = latex2exp::TeX(long_labels_for_parms[pop_id])) + 
      scale_x_continuous(breaks = seq(-10,10,5))  + # see above
     # the_y_scale +
  theme_classic()+
  theme(plot.title = element_text(hjust=0.5))+
 # scale_color_manual(values = c(rev(gray.colors(4))[c(2,4)],1), name = "Type") +
  scale_color_manual(values = unname(colors_for_gg_premium2), name = "Premium") +
  scale_linetype_manual(values = c(1, 2), name = "d") +
  scale_alpha_manual(values = c(0.75, 1), name = "d") +
  scale_linewidth_manual(values = c(1, 0.55), name = 'd') 

  })%>% ggpubr::ggarrange(plotlist = .,
                           nrow = 1, ncol=3,
                           widths = 12, heights = 1,
                           common.legend = T,
                           legend = 'right'))

ggsave(filename = "figs/graph_mean_prem_paid.pdf",
       plot = to_save_meanprem,
       height = 3,
       width = 9,
       units = "in",
       device = "pdf", dpi = 500)

```

```{r meanpremcor}

(to_save_meanprem_cor <- names(df_to_g_A1)[1:3] %>% lapply(function(pop_name){

premB_bycomp <- rep(0, n/10)
premB_bycomp[which(test[[pop_name]]$A==1)] <-  scores_A1[[pop_name]]$SB(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==1)]
premB_bycomp[which(test[[pop_name]]$A==0)] <-  scores_A0[[pop_name]]$SB(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==0)]

premC_bycomp <- rep(0, n/10)
premC_bycomp[which(test[[pop_name]]$A==1)] <-  scores_A1[[pop_name]]$SC(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==1)]
premC_bycomp[which(test[[pop_name]]$A==0)] <-  scores_A0[[pop_name]]$SC(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==0)]

xseq <- seq(-10.5,12, by=0.5)
Xdiscretized <- cut(test[[pop_name]]$X, xseq)
midpoint.vec <- xseq[-length(xseq)] + diff(xseq)/2
names(midpoint.vec) <- levels(Xdiscretized)
Xmid <- midpoint.vec[Xdiscretized]
  
  pop_id <- which(names(df_to_g_A1) == pop_name)
    
    # keep only axis for last plot
    if(which(pop_name == names(df_to_g_A1)) %in% c(1,4)){
      the_y_label <- latex2exp::TeX("Premium")
      the_y_scale <- scale_y_continuous()
      the_x_label <- latex2exp::TeX("x")
      } else { 
      the_y_label <- NULL
      the_y_scale <- scale_y_continuous(labels = NULL)
      the_x_label <- latex2exp::TeX("x")
      }
  
aggregate(cbind(Best, Corrective)~Xdisc+D, FUN=mean,
          data=test[[pop_name]]%>% mutate(Best = premB_bycomp, 
                                          Corrective = premC_bycomp,
                                          Xdisc = Xmid))%>%
  reshape2::melt(measure.vars = c("Best", "Corrective"))%>%
    filter(Xdisc >= -8, Xdisc <= 10) %>%
ggplot(aes(x=Xdisc, y=value,
           col=variable,
           lty=factor(D),
           alpha=factor(D),
           linewidth=factor(D)))+
  geom_line(alpha=0.75)+ 
  labs(x = the_x_label,
       y = the_y_label,
       title = latex2exp::TeX(long_labels_for_parms[pop_id])) + 
      scale_x_continuous(breaks = seq(-10,10,5))  + # see above
     # the_y_scale +
  theme_classic()+
  theme(plot.title = element_text(hjust=0.5))+
  scale_color_manual(values = colorspace::darken(unname(colors_for_gg_premium[c(1, 4)]), 0.2), name = "Premium") +
 # scale_color_manual(values = unname(colors_for_gg_premium2), name = "Premium") +
  scale_linetype_manual(values = c(1, 2), name = "d") +
  scale_alpha_manual(values = c(0.75, 1), name = "d") +
  scale_linewidth_manual(values = c(1, 0.55), name = 'd') 

  })%>% ggpubr::ggarrange(plotlist = .,
                           nrow = 1, ncol=3,
                           widths = 12, heights = 1,
                           common.legend = T,
                           legend = 'right'))

ggsave(filename = "figs/graph_mean_prem_paid_cor.pdf",
       plot = to_save_meanprem_cor,
       height = 3,
       width = 9,
       units = "in",
       device = "pdf", dpi = 500)

```

Version in French for a presentation (not used).

```{r}
to_save_meanprem_list_forpres <- names(df_to_g_A1)[1:3] %>% lapply(function(pop_name){

premB_bycomp <- rep(0, n/10)
premB_bycomp[which(test[[pop_name]]$A==1)] <-  scores_A1[[pop_name]]$SB(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==1)]
premB_bycomp[which(test[[pop_name]]$A==0)] <-  scores_A0[[pop_name]]$SB(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==0)]

premA_bycomp <- rep(0, n/10)
premA_bycomp[which(test[[pop_name]]$A==1)] <-  scores_A1[[pop_name]]$SA(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==1)]
premA_bycomp[which(test[[pop_name]]$A==0)] <-  scores_A0[[pop_name]]$SA(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==0)]

premA_market <- scores[[pop_name]]$SA(x = test[[pop_name]]$X, d=test[[pop_name]]$D)

xseq <- seq(-10.5,12, by=0.5)
Xdiscretized <- cut(test[[pop_name]]$X, xseq)
midpoint.vec <- xseq[-length(xseq)] + diff(xseq)/2
names(midpoint.vec) <- levels(Xdiscretized)
Xmid <- midpoint.vec[Xdiscretized]
  
  pop_id <- which(names(df_to_g_A1) == pop_name)
    
    # keep only axis for last plot
    if(which(pop_name == names(df_to_g_A1)) %in% c(1,4)){
      the_y_label <- latex2exp::TeX("Valeur de la prime")
      the_y_scale <- scale_y_continuous()
      the_x_label <- latex2exp::TeX("x")
      } else { 
      the_y_label <- NULL
      the_y_scale <- scale_y_continuous(labels = NULL)
      the_x_label <- latex2exp::TeX("x")
      }
  
aggregate(cbind(Best, Aware, Aware_market)~Xdisc+D, FUN=mean,
          data=test[[pop_name]]%>% mutate(Aware = premA_bycomp, 
                                          Aware_market = premA_market,
                                          Best = premB_bycomp, 
                                          Xdisc = Xmid))%>%
  reshape2::melt(measure.vars = c("Best", "Aware", "Aware_market"))%>%
    filter(Xdisc >= -8, Xdisc <= 10) %>%
ggplot(aes(x=Xdisc, y=value,
           col=variable,
           lty=factor(D),
           linewidth=factor(D)))+
  geom_line(alpha=0.75)+ 
  labs(x = the_x_label,
       y = the_y_label,
       title = latex2exp::TeX(long_labels_for_parms[pop_id])) + 
      scale_x_continuous(breaks = seq(-10,10,5))  + # see above
     # the_y_scale +
  theme_minimal()+
  theme(plot.title = element_text(hjust=0.5))+
#  scale_color_manual(values = c(rev(gray.colors(4))[c(2,4)],1), name = "Type") +
  scale_color_manual(values = c(1, 2, gray.colors(3)[2]), name = "Prime", 
                     labels=c("Précise", "Consciente par ass.", "Consciente complet")) +
  scale_linetype_manual(values = c(1, 2), name = "D") +
  scale_linewidth_manual(values = c(1, 0.8), name = 'd') 

  })

(to_save_meanprem_for_pres <- to_save_meanprem_list_forpres %>% ggpubr::ggarrange(plotlist = .,
                           nrow = 1, ncol=3,
                           widths = 12, heights = 1,
                           common.legend = T,
                           legend = 'right'))

to_save_meanprem_list_forpres[[1]]

```

# Fairness Criteria

In this section, we assess whether the fairness criteria are verified.

## Big fairness table 

```{r}

the_raw_content_for_big_table <- setNames(nm = names(test)[1:3]) %>% lapply(function(pop_name){
  setNames(nm = c('1', 'full')) %>%  lapply(function(pop_A_ref){
    setNames(nm = c('1', '0', 'unbiased', 'mixture')) %>%  lapply(function(pop_A_train){
          
      
          full_local_test <- test[[pop_name]]
          local_test_A1 <- full_local_test[full_local_test$A == 1, ]
          
          if(pop_A_ref == '1'){
            local_test <- local_test_A1
          } else {
            local_test <- full_local_test
          }
          
          ## for balancing
          mean_Y_loc <- mean(local_test$Y)
          mean_Y_full <- mean(full_local_test$Y)
          
          if(pop_A_train == '1'){
            scores_to_compute <- scores_A1[[pop_name]] 
            } else if(pop_A_train == '0'){
              scores_to_compute <- scores_A0[[pop_name]] 
            } else {
            scores_to_compute <- scores[[pop_name]]
          }
          
          the_preds_table_local <- setNames(nm = c('SB', 'SA', 'SC', 'SA_unb')) %>% sapply(function(the_score){
            if(the_score == 'SA_unb' & pop_A_ref == 'full') return(scores[[pop_name]][['SA']](x = local_test$X, d = local_test$D))
            if(the_score == 'SA_unb' & pop_A_ref == '1') return(scores_A1[[pop_name]][['SA']](x = local_test$X, d = local_test$D))
            scores_to_compute[[the_score]](x = local_test$X,
                                           d = local_test$D)
          }) %>% as.data.frame()
          
          the_preds_table_local_unb <- setNames(nm = c('SB', 'SA', 'SC', 'SA_unb')) %>% sapply(function(the_score){
            if(the_score == 'SA_unb' & pop_A_ref == 'full') return(scores[[pop_name]][['SA']](x = local_test$X, d = local_test$D))
            if(the_score == 'SA_unb' & pop_A_ref == '1') return(scores_A1[[pop_name]][['SA']](x = local_test$X, d = local_test$D))
            scores_to_compute[[the_score]](x = local_test$X,
                                           d = local_test$D)
          }) %>% as.data.frame()
          
          factor_balance <- mean_Y_loc/apply(the_preds_table_local, 2, mean)
          factor_balance_unb <- mean_Y_full/apply(the_preds_table_local_unb, 2, mean)
          
          the_preds_table_full <- setNames(nm = c('SB', 'SA', 'SC', 'SA_unb')) %>% sapply(function(the_score){
            if(the_score == 'SA_unb' & pop_A_ref == 'full') return(scores[[pop_name]][['SA']](x = full_local_test$X, d = full_local_test$D))
            if(the_score == 'SA_unb' & pop_A_ref == '1') return(scores_A1[[pop_name]][['SA']](x = full_local_test$X, d = full_local_test$D))
            scores_to_compute[[the_score]](x = full_local_test$X,
                                           d = full_local_test$D)
          }) %>% as.data.frame()
          
          the_preds_table_full_unb <- setNames(nm = c('SB', 'SA', 'SC', 'SA_unb')) %>% sapply(function(the_score){
            if(the_score == 'SA_unb' & pop_A_ref == 'full') return(scores[[pop_name]][['SA']](x = full_local_test$X, d = full_local_test$D))
            if(the_score == 'SA_unb' & pop_A_ref == '1') return(scores_A1[[pop_name]][['SA']](x = full_local_test$X, d = full_local_test$D))
            scores[[pop_name]][[the_score]](x = full_local_test$X,
                                           d = full_local_test$D)
          }) %>% as.data.frame()
          
          
          the_preds_table_mixture <- setNames(nm = c('SB', 'SA', 'SC', 'SA_unb')) %>% sapply(function(the_score){
            if(the_score == 'SA_unb') return(scores[[pop_name]][['SA']](x = full_local_test$X, d = full_local_test$D))
              
            prem_A1 <- scores_A1[[pop_name]][[the_score]](x = full_local_test$X,
                                                  d = full_local_test$D) * factor_balance[the_score]
            prem_A0 <- scores_A0[[pop_name]][[the_score]](x = full_local_test$X,
                                                  d = full_local_test$D) * factor_balance[the_score]
            1:nrow(full_local_test) %>% sapply(function(i){
              if(full_local_test$A[i] == 1){
                return(prem_A1[i])
              } else if(full_local_test$A[i] == 0){
                return(prem_A0[i])
              }
            })
            }) %>% as.data.frame()
          
        return(
          list('loc_data' = local_test, 
               'full_data' = full_local_test, 
               'loc_table' = sweep(the_preds_table_local, 2, factor_balance, '*'),
               'loc_table_unb' = sweep(the_preds_table_local, 2, factor_balance_unb, '*'),
               'full_table' =  sweep(the_preds_table_full, 2, factor_balance, '*'),
               'full_table_unb' = sweep(the_preds_table_full, 2, factor_balance_unb, '*'), 
               'mixture_table' =  sweep(the_preds_table_mixture, 2, factor_balance_unb, '*'))
        )  
    })
  })
})

the_tables <- setNames(nm = names(test)[1:3]) %>%  lapply(function(scenario){
  
to_fill <- data.frame('i' = rep(1:6, 3),
                      'scenario' = rep(scenario, (2 + 4)*3),
                      'qty' = c(rep('LR', 6), rep('Proxy', 6), rep('DP', 6)),
           'pop_ref' = rep(c(rep('1', 2), rep('full', 4)), 3),
           'mod_type' = rep(c('1', 'unbiased', '1',
                              '0', 'unbiased', 'mixture'), 3))

to_fill$SB <- rep(NA, nrow(to_fill))
to_fill$SA <- rep(NA, nrow(to_fill))
to_fill$SC <- rep(NA, nrow(to_fill))

wasserstein_by_group <- function(values, group) {
  # Check inputs
  if (length(values) != length(group)) stop("Length mismatch between values and group.")
  if (length(unique(group)) != 2) stop("Group must be binary.")
  
  # Convert group to factor with two levels
  group <- as.factor(group)
  
  # Split values by group
  values0 <- values[group == levels(group)[1]]
  values1 <- values[group == levels(group)[2]]
  
  # Load transport package for wasserstein1d
  if (!requireNamespace("transport", quietly = TRUE)) {
    install.packages("transport")
  }
  library(transport)
  
  # Compute 1D Wasserstein distance
  return(wasserstein1d(values0, values1))
}

best_shift_mse_optimize <- function(x, y) {
  if (length(x) != length(y)) stop("x and y must have the same length")
  
  # Define the MSE function to minimize
  mse_function <- function(c) {
    mean((x + c - y)^2)
  }
  
  # Optimize over a reasonable range (e.g., -1000 to 1000)
  result <- optimize(mse_function, interval = c(-1e3, 1e3))
  
  # Return both optimal constant and minimum MSE
  return(result$minimum)
}


for (i in unique(to_fill$i)) {
  scenario <- to_fill[i, 'scenario']
  ref_pop <- to_fill[i, 'pop_ref']
  model <- to_fill[i, 'mod_type']
  
  if(ref_pop == '1'){
    pop_eval_loc <- the_raw_content_for_big_table[[scenario]][[ref_pop]][[model]]$loc_data
    if(model == 'unbiased'){
      the_preds_table <- the_raw_content_for_big_table[[scenario]][[ref_pop]][[model]]$loc_table
    } else {
      the_preds_table <- the_raw_content_for_big_table[[scenario]][[ref_pop]][[model]]$loc_table_unb
    }
  } else {
    pop_eval_loc <- the_raw_content_for_big_table[[scenario]][[ref_pop]][[model]]$full_data
    if(model  == 'mixture'){
      the_preds_table <- the_raw_content_for_big_table[[scenario]][[ref_pop]][[model]]$mixture_table
    } else if(model  == '1'){
      the_preds_table <- the_raw_content_for_big_table[[scenario]][[ref_pop]][[model]]$full_table
    } else {
      the_preds_table <- the_raw_content_for_big_table[[scenario]][[ref_pop]][[model]]$full_table_unb
    }
  }
  
  
  table_to_return <- setNames(nm = c('SB', 'SA', 'SC')) %>% sapply(function(score){
    ## Loss ratio parity
    LR <- pop_eval_loc$Y/the_preds_table[[score]]
    LR_par <- wasserstein_by_group(LR, group = pop_eval_loc$D)
    
    ## Demographic parity
    demo_par <- wasserstein_by_group(the_preds_table[[score]], group = pop_eval_loc$D)
    
    ## PD metric... 
    const_opt <- best_shift_mse_optimize(the_preds_table[[score]], the_preds_table[['SA_unb']])
    proxy <- wasserstein_by_group(the_preds_table[[score]] + const_opt - the_preds_table[['SA_unb']], 
                         group = pop_eval_loc$D)
    
    names_to_output <- c('LR', 'Proxy', 'DP')
    setNames(c(LR_par, proxy, demo_par),
             nm = names_to_output)
  })
  
  to_fill[to_fill$i == i, c('SB', 'SA', 'SC')] <- table_to_return
}

return(to_fill)

})


the_tables %>% do.call(rbind, .) %>% 
  filter(!(pop_ref == 'full' & mod_type == '0'),
         !(pop_ref == '1' & mod_type == 'unbiased')) %>% 
  xtable::xtable(digits = 3)
```

```{r}
saveRDS(the_tables %>% do.call(rbind, .), 'preds/metrics_tables')
```


## Aware premium

### Premium Independence criterion

```{r AwareIndep, echo=FALSE, fig.width=12, fig.height=10}


# 
# 
# (to_save_SA_indep <- names(df_to_g_A1) %>% lapply(function(pop_name){
# premA_bycomp <- rep(0, n/10)
# premA_bycomp[which(test[[pop_name]]$A==1)] <-  scores_A1[[pop_name]]$SA(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==1)]
# premA_bycomp[which(test[[pop_name]]$A==0)] <-  scores_A0[[pop_name]]$SA(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==0)]
# 
# melted_version <- test[[pop_name]] %>% mutate(premA_bycomp = premA_bycomp,premA = scores[[pop_name]]$SA(x = test[[pop_name]]$X, d=test[[pop_name]]$D)) %>%
#   reshape2::melt(measure.vars = c("premA_bycomp", "premA")) %>% 
#     mutate(variable = factor(variable,
#                              levels = c("premA_bycomp", "premA"),
#                              labels = c("Portfolio-specific", "Market")))%>%
#   mutate(premAware = value)
# 
# ggplot(melted_version, aes(x=premAware, fill=factor(D), col=factor(D)))+
#   geom_density(alpha=0.5)+
#   facet_grid(~variable)+
#   theme_classic()+
#   scale_color_manual(values=colors_for_gg_D)+
#   scale_fill_manual(values=colors_for_gg_D)+
#   ggtitle(long_labels_for_parms[pop_name])+
#   labs(x="Aware premium", fill="D", col="D")
# 
# }))

```


### Loss Ratio Independence

It is seen that the aware by company is closer to actuarial fairness than when using the complete market:

```{r, fig.height=10, echo=FALSE}
(to_save_LR_indep <- names(df_to_g_A1) %>% lapply(function(pop_name){
  
premA_bycomp <- rep(0, n/10)
premA_bycomp[which(test[[pop_name]]$A==1)] <-  scores_A1[[pop_name]]$SA(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==1)]
premA_bycomp[which(test[[pop_name]]$A==0)] <-  scores_A0[[pop_name]]$SA(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==0)]

melted_version <- test[[pop_name]] %>% mutate(premA = scores[[pop_name]]$SA(x = test[[pop_name]]$X,
                                                                            d=test[[pop_name]]$D))%>%
  mutate(LRA = Y/premA, LRA_bycomp = Y/premA_bycomp)  %>%
  reshape2::melt(measure.vars = c("LRA_bycomp", "LRA")) %>% 
    mutate(variable = factor(variable,
                             levels = c("LRA_bycomp", "LRA"),
                             labels = c("Portfolio-specific", "Market")))%>%
  mutate(LossRatio = value)

ggplot(melted_version, aes(x=LossRatio, fill=factor(D), col=factor(D)))+
  geom_density(alpha=0.5)+
  facet_grid(~variable)+
  theme_classic()+
  scale_color_manual(values=colors_for_gg_D)+
  scale_fill_manual(values=colors_for_gg_D)+
  ggtitle(long_labels_for_parms[pop_name])+
  labs(x="Loss ratio", fill="D", col="D") + 
  scale_x_continuous(limits = c(0.7, 1.3),
                     breaks = c(0.8, 1, 1.2)) 

})%>% ggpubr::ggarrange(plotlist = .,
                           nrow = 3, ncol=2,
                           widths = 15, heights = 1,
                           common.legend = T,
                           legend = 'right'))


ggsave(filename = "figs/graph_LRAware.pdf",
       plot = to_save_LR_indep,
       height = 7,
       width = 11,
       units = "in",
       device = "pdf", dpi = 500)

```

### Separation criterion

Here it is also visible:

```{r, fig.width=12}
vec_cut <- quantile(valid$original$Y, seq(0,1,0.1)) +c(-0.5, rep(0,9),0.5)


(tosave_Aware_givenDY <- names(df_to_g_A1) %>% lapply(function(pop_name){
groupy <- cut(test[[pop_name]]$Y, vec_cut)

premA_bycomp <- rep(0, n/10)
premA_bycomp[which(test[[pop_name]]$A==1)] <-  scores_A1[[pop_name]]$SA(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==1)]
premA_bycomp[which(test[[pop_name]]$A==0)] <-  scores_A0[[pop_name]]$SA(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==0)]

melted_version <- test[[pop_name]] %>% mutate(premA_bycomp = premA_bycomp, groupy=groupy, premA = scores[[pop_name]]$SA(x = test[[pop_name]]$X, d=test[[pop_name]]$D)) %>%
  filter(Y>vec_cut[3],Y<=vec_cut[9]) %>% droplevels() %>%
  reshape2::melt(measure.vars = c("premA_bycomp", "premA")) %>% 
    mutate(variable = factor(variable,
                             levels = c("premA_bycomp", "premA"),
                             labels = c("Portfolio-specific", "Market")))%>%
  mutate(premAware=value)


ggplot(melted_version, aes(x=premAware, fill=factor(D), col=factor(D)))+
  geom_density(alpha=0.5)+theme_bw()+facet_grid(groupy~variable)+
  theme_minimal()+
    scale_color_manual(values=colors_for_gg_D)+
    scale_fill_manual(values=colors_for_gg_D)+
  ggtitle(long_labels_for_parms[pop_name])
})%>%
ggpubr::ggarrange(plotlist = .,
                           ncol = 6, nrow=1,
                           widths = 23, heights = 1,
                           common.legend = T,
                           legend = 'right'))

```

## Corrective Premium fairness criteria

### Premium independence criterion

```{r, echo=FALSE, fig.width=12, fig.height=10}

(to_save_SC_indep <- names(df_to_g_A1) %>% lapply(function(pop_name){
premC_bycomp <- rep(0, n/10)

v0 <- valid[[pop_name]][valid[[pop_name]]$A==0, ]
v1 <- valid[[pop_name]][valid[[pop_name]]$A==1, ]
v <- valid[[pop_name]]

pb_0 <- sum(v0$Y) / sum(scores_A0[[pop_name]]$SC(x = v0$X, d=v0$D))
pb_1 <- sum(v1$Y) / sum(scores_A1[[pop_name]]$SC(x = v1$X, d=v1$D))
mb <- sum(v0$Y) / sum(scores[[pop_name]]$SC(x = v$X, d=v$D))

premC_bycomp[which(test[[pop_name]]$A==1)] <-  scores_A1[[pop_name]]$SC(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==1)] * pb_0
premC_bycomp[which(test[[pop_name]]$A==0)] <-  scores_A0[[pop_name]]$SC(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==0)] * pb_1
premC <- scores[[pop_name]]$SC(x = test[[pop_name]]$X, d=test[[pop_name]]$D) * mb


melted_version <- test[[pop_name]] %>% mutate(premC_bycomp = premC_bycomp,premC = scores[[pop_name]]$SC(x = test[[pop_name]]$X, d=test[[pop_name]]$D)) %>%
  reshape2::melt(measure.vars = c("premC_bycomp", "premC")) %>% 
    mutate(variable = factor(variable,
                             levels = c("premC_bycomp", "premC"),
                             labels = c("Portfolio-specific", "Market")))%>%
  mutate(premCorrective = value)

ggplot(melted_version, aes(x=premCorrective, fill=factor(D), col=factor(D)))+
  geom_density(alpha=0.5)+
  facet_grid(~variable)+
  theme_classic()+
  scale_x_continuous(limits = c(80, 140),
                     breaks = c(90, 110, 130)) + 
  scale_color_manual(values=colors_for_gg_D)+
    scale_fill_manual(values=colors_for_gg_D)+
  ggtitle(long_labels_for_parms[pop_name])+
  labs(x="Corrective premium", fill="D", col="D")

})%>% ggpubr::ggarrange(plotlist = .,
                           nrow = 3, ncol=2,
                           widths = 15, heights = 1,
                           common.legend = T,
                           legend = 'right'))

ggsave(filename = "figs/graph_Corrective.pdf",
       plot = to_save_SC_indep,
       height = 7,
       width = 11,
       units = "in",
       device = "pdf", dpi = 500)

```

```{r, echo=FALSE, fig.width=12, fig.height=10}

to_save_SC_indep2 <- function(pop_name){
premC_bycomp <- rep(0, n/10)

v0 <- valid[[pop_name]][valid[[pop_name]]$A==0, ]
v1 <- valid[[pop_name]][valid[[pop_name]]$A==1, ]
v <- valid[[pop_name]]

pb_0 <- sum(v0$Y) / sum(scores_A0[[pop_name]]$SC(x = v0$X, d=v0$D))
pb_1 <- sum(v1$Y) / sum(scores_A1[[pop_name]]$SC(x = v1$X, d=v1$D))
mb <- sum(v$Y) / sum(scores[[pop_name]]$SC(x = v$X, d=v$D))

premC_bycomp[which(test[[pop_name]]$A==1)] <-  scores_A1[[pop_name]]$SC(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==1)] * pb_0
premC_bycomp[which(test[[pop_name]]$A==0)] <-  scores_A0[[pop_name]]$SC(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==0)] * pb_1
premC <- scores[[pop_name]]$SC(x = test[[pop_name]]$X, d=test[[pop_name]]$D) * mb


df_to_g_bycomp <- data.frame(muCA = premC_bycomp, 
                      muC = premC,
                      'D' = test[[pop_name]]$D,
                      'A' = c(test[[pop_name]]$A))

df_to_g_market <- df_to_g_bycomp %>% mutate(A = 2)


appender <- function(string) latex2exp::TeX(string) 

rbind(df_to_g_bycomp, df_to_g_market) %>% 
  mutate(A = factor(A, levels = c(0, 2, 1),
                    labels = c('$A=0$', 'Market', '$A=1$'))) %>% 
  reshape2::melt(measure.vars = c('muCA', 'muC')) %>%
  mutate(variable = factor(variable, levels = c('muCA', 'muC'),
                           labels = c('$S = \\mu^C_{pb}(X, d, A)$',
                                                            '$S = \\mu^C_{mb}(X, d)$')
                           )) %>% 
ggplot(aes(x=value, fill=factor(D), col=factor(D), lty = factor(D), size = factor(D)))+
  geom_density(alpha=0.4, bw = 1.5)+
  facet_grid(cols = vars(A), rows = vars(variable),
             labeller = as_labeller(appender, default = label_parsed))+
  scale_x_continuous(limits = c(80, 140),
                     breaks = c(90, 110, 130)) + 
  theme_classic()+
  scale_color_manual(values=colors_for_gg_D, name = 'd')+
    scale_fill_manual(values=colors_for_gg_D, name = 'd')+
  scale_linetype_manual(values=c('solid', '33'), name = 'd')+
  scale_size_manual(values=c(1, 0.7), name = 'd')+
  #ggtitle(long_labels_for_parms[pop_name])+
  labs(x="s",
       y = latex2exp::TeX('$\\hat{f}_{S|D, A}(s|d, a)$'),
       fill="D", col="D") 
}

to_save_SC_indep2('original')

ggsave(filename = "figs/graph_Corrective2.pdf",
       plot = to_save_SC_indep2('original'),
       height = 3.25,
       width = 8,
       units = "in",
       device = "pdf", dpi = 500)

```

```{r, echo=FALSE, fig.width=12, fig.height=10}

(to_save_SC_indep_full <- names(df_to_g_A1) %>% lapply(function(pop_name){
premC_bycomp <- rep(0, n/10)

v0 <- valid[[pop_name]][valid[[pop_name]]$A==0,]
v1 <- valid[[pop_name]][valid[[pop_name]]$A==1,]
v <- valid[[pop_name]]

pb_0 <- sum(v0$Y) / sum(scores_A0[[pop_name]]$SC(x = v0$X, d=v0$D))
pb_1 <- sum(v1$Y) / sum(scores_A1[[pop_name]]$SC(x = v1$X, d=v1$D))
mb <- sum(v$Y) / sum(scores[[pop_name]]$SC(x = v$X, d=v$D))

premC_bycomp[which(test[[pop_name]]$A==1)] <-  scores_A1[[pop_name]]$SC(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==1)] * pb_0
premC_bycomp[which(test[[pop_name]]$A==0)] <-  scores_A0[[pop_name]]$SC(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==0)] * pb_1
premC <- scores[[pop_name]]$SC(x = test[[pop_name]]$X, d=test[[pop_name]]$D) * mb

df_to_g_bycomp <- data.frame(muCA = premC_bycomp, 
                      muC = premC,
                      'D' = test[[pop_name]]$D,
                      'A' = c(test[[pop_name]]$A))

df_to_g_market <- df_to_g_bycomp %>% mutate(A = 2)


appender <- function(string) latex2exp::TeX(string) 

rbind(df_to_g_bycomp, df_to_g_market) %>% 
  mutate(A = factor(A, levels = c(0, 2, 1),
                    labels = c('$A=0$', 'Market', '$A=1$'))) %>% 
  reshape2::melt(measure.vars = c('muCA', 'muC')) %>%
  mutate(variable = factor(variable, levels = c('muCA', 'muC'),
                           labels = c('$S = \\mu^C_{pb}(X, d|A)$',
                                                            '$S = \\mu^C_{mb}(X, d)$')
                           )) %>% 
ggplot(aes(x=value, fill=factor(D), col=factor(D)))+
  geom_density(alpha=0.5, bw = 2)+
  facet_grid(cols = vars(A), rows = vars(variable),
             labeller = as_labeller(appender, default = label_parsed),
             scales = "free_x", space = "free_x")+
  theme_classic()+
  scale_color_manual(values=colors_for_gg_D, name = 'd')+
    scale_fill_manual(values=colors_for_gg_D, name = 'd')+
  scale_y_continuous(breaks = c(0, 0.02, 0.04)) + 
  ggtitle(long_labels_for_parms[pop_name])+
  labs(x="s",
       y = latex2exp::TeX('$\\hat{f}_{S|D, A}(s|d, a)$'),
       fill="D", col="D") + 
  theme(strip.text.y = element_text(size = 6),
        axis.text.x = element_text(size = 6))
})%>% ggpubr::ggarrange(plotlist = .,
                           nrow = 3, ncol=2,
                           widths = 15, heights = 1,
                           common.legend = T,
                           legend = 'right'))

ggsave(filename = "figs/graph_Corrective_full.pdf",
       plot = to_save_SC_indep_full,
       height = 7,
       width = 11,
       units = "in",
       device = "pdf", dpi = 500)

```

### Loss Ratio Independence

Closer to actuarial fairness than when using the complete market:

```{r, fig.height=10, echo=FALSE}
(to_save_LRC_indep <- names(df_to_g_A1) %>% lapply(function(pop_name){
  
premC_bycomp <- rep(0, n/10)
premC_bycomp[which(test[[pop_name]]$A==1)] <-  scores_A1[[pop_name]]$SC(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==1)]
premC_bycomp[which(test[[pop_name]]$A==0)] <-  scores_A0[[pop_name]]$SC(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==0)]

melted_version <- test[[pop_name]] %>% mutate(premC = scores[[pop_name]]$SC(x = test[[pop_name]]$X, d=test[[pop_name]]$D))%>%
  mutate(LRC = Y/premC, LRC_bycomp = Y/premC_bycomp)  %>%
  reshape2::melt(measure.vars = c("LRC_bycomp", "LRC")) %>% 
    mutate(variable = factor(variable,
                             levels = c("LRC_bycomp", "LRC"),
                             labels = c("Portfolio-specific", "Market")))%>%
  mutate(LossRatio = value)

ggplot(melted_version, aes(x=LossRatio, fill=factor(D), col=factor(D)))+
  geom_density(alpha=0.5)+
  facet_grid(~variable)+
  theme_classic()+
  scale_color_manual(values=colors_for_gg_D)+
    scale_fill_manual(values=colors_for_gg_D)+
    scale_linetype_manual(values=1:2, name = 'd')+
  ggtitle(long_labels_for_parms[pop_name])+
  labs(x="Loss ratio", fill="D", col="D")+
  scale_x_continuous(limits = c(0.65, 1.35),
                     breaks = c(0.8, 1, 1.2)) 

})%>% ggpubr::ggarrange(plotlist = .,
                           nrow = 3, ncol=2,
                           widths = 15, heights = 1,
                           common.legend = T,
                           legend = 'right'))


ggsave(filename = "figs/graph_LRCorrective.pdf",
       plot = to_save_LRC_indep,
       height = 7,
       width = 11,
       units = "in",
       device = "pdf", dpi = 500)

```




# Results on test set

Here we try to see the aggregate LR and Average premiums by group. We do not keep this representation in the end.

```{r, fig.width=12, fig.height=9}

pop_name <- "original"

testLRandprem <- lapply(names(sims) ,function(pop_name) {
  test_premA_bycomp <- rep(0, n/10)
test_premA_bycomp[which(test[[pop_name]]$A==1)] <-  scores_A1[[pop_name]]$SA(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==1)]
test_premA_bycomp[which(test[[pop_name]]$A==0)] <-  scores_A0[[pop_name]]$SA(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==0)]

test_premApp_bycomp <- rep(0, n/10)
test_premApp_bycomp[which(test[[pop_name]]$A==1)] <-  scores_A1[[pop_name]]$SA.pp(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==1)]
test_premApp_bycomp[which(test[[pop_name]]$A==0)] <-  scores_A0[[pop_name]]$SA.pp(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==0)]

test_premU_bycomp <- rep(0, n/10)
test_premU_bycomp[which(test[[pop_name]]$A==1)] <-  scores_A1[[pop_name]]$SU(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==1)]
test_premU_bycomp[which(test[[pop_name]]$A==0)] <-  scores_A0[[pop_name]]$SU(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==0)]

test_premBE_bycomp <- rep(0, n/10)
test_premBE_bycomp[which(test[[pop_name]]$A==1)] <-  scores_A1[[pop_name]]$SB(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==1)]
test_premBE_bycomp[which(test[[pop_name]]$A==0)] <-  scores_A0[[pop_name]]$SB(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==0)]

test_wprem <- test[[pop_name]] %>% mutate(premA = test_premA_bycomp, 
                            premA.pp = test_premApp_bycomp, 
                            premU = test_premU_bycomp,
                            premBE = test_premBE_bycomp,
                            premAmark = scores[[pop_name]]$SA(x = test[[pop_name]]$X,
                                                               d=test[[pop_name]]$D))

LossRatios <- test_wprem %>% 
  aggregate(cbind(premBE, premU, premA, premA.pp, premAmark, Y)~D, FUN=sum) %>%
  mutate(LRBE = Y/premBE, LRU = Y/premU, LRA = Y/premA, 
         LRpp = Y/premA.pp, LRmarket = Y/premAmark)%>%
  select(D, LRBE, LRU, LRA, LRpp, LRmarket)%>%
  rename(BE=LRBE, Unaware=LRU, Aware.bycomp = LRA, Aware.pp = LRpp, Aware.market = LRmarket)%>%
reshape2::melt(id.vars = 1, measure.vars = 2:6, variable.name = "family", value.name="LR")

# test_wprem %>%
# aggregate(cbind(premBE, premU, premA, premA.pp, premAmark, Y)~D+A, FUN=sum) %>%
#   mutate(LRBE = Y/premBE, LRU = Y/premU, LRA = Y/premA, 
#          LRpp = Y/premA.pp, LRmarket = Y/premAmark)

#test_wprem %>%
#  aggregate(cbind(premBE, premU, premA, premA.pp, premAmark)~D+A, FUN=mean)

AvgPrem <- test_wprem %>%
  aggregate(cbind(premBE, premU, premA, premA.pp, premAmark)~D, FUN=mean)%>%
  rename(BE=premBE, Unaware=premU, Aware.bycomp = premA, Aware.pp = premA.pp, Aware.market = premAmark)%>%
reshape2::melt(id.vars = 1, measure.vars = 2:6, variable.name = "family", value.name="AvgPrem")

merge(AvgPrem, LossRatios)%>%
  reshape2::melt(id.vars=1:2, measure.vars=3:4)})

names(testLRandprem) <- names(sims)


listofplotLRPREM <- names(testLRandprem) %>% lapply(function(pop_name){ 
  ggplot(testLRandprem[[pop_name]], aes(x=family, fill=factor(D), y = value))+
  geom_bar(stat="identity", position=position_dodge())+
  facet_wrap(~variable, scales="free_y")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  labs(title = latex2exp::TeX(long_labels_for_parms[pop_name])) })

ggpubr::ggarrange(plotlist=listofplotLRPREM,
                          ncol = 3, nrow=2,
                           widths = 15, heights = 1,
                           common.legend = T,
                           legend = 'right')
```


## other graphs


```{r}
names(df_to_g_A1) %>% lapply(function(pop_name){
pdx_test_byComp <- rep(0, n/10)
pdx_test_byComp[which(test[[pop_name]]$A==0)] <-
  pdx_lgb_A0[[pop_name]]$preds$test[which(test[[pop_name]]$A==0)]
pdx_test_byComp[which(test[[pop_name]]$A==1)] <-
  pdx_lgb_A1[[pop_name]]$preds$test[which(test[[pop_name]]$A==1)]

test[[pop_name]]%>% mutate(pdx = pdx_test_byComp, D= factor(D)) %>%
  ggplot(aes(x=X, colour = D, y = pdx))+
  geom_point(alpha=0.5)+
  theme_minimal()+
   labs(x = latex2exp::TeX("$x$"),
       y = latex2exp::TeX("$P(D=1|X=x,A)$"),
       title = latex2exp::TeX(long_labels_for_parms[pop_name])) }
)%>% ggpubr::ggarrange(plotlist = .,
                           nrow = 3, ncol=2,
                           widths = 15, heights = 1,
                           common.legend = T,
                           legend = 'right')

names(df_to_g_A1) %>% lapply(function(pop_name){
pdmarg_test_byComp <- rep(0, n/10)
pdmarg_test_byComp[which(test[[pop_name]]$A==0)] <-
  marg_dist_A0[[pop_name]][2]
pdmarg_test_byComp[which(test[[pop_name]]$A==1)] <-
  marg_dist_A1[[pop_name]][2]

test[[pop_name]]%>% mutate(pdmarg = pdmarg_test_byComp, D= factor(D)) %>%
  ggplot(aes(y=X, x = factor(pdmarg)))+
  geom_boxplot()+
  theme_minimal()+
   labs(y = latex2exp::TeX("$x$"),
       x = latex2exp::TeX("$P(D=1|A)$"),
       title = latex2exp::TeX(long_labels_for_parms[pop_name])) }
)%>% ggpubr::ggarrange(plotlist = .,
                           nrow = 3, ncol=2,
                           widths = 15, heights = 1,
                           common.legend = T,
                           legend = 'right')
```

```{r}

```


# Premium rebalancing

I want to compare the SA, the SA.pp and the SA.pp rebalanced.

```{r}

sss <- scores_A0[[pop_name]]$SA.pp(sims[[pop_name]]$X, sims[[pop_name]]$D)[which(sims[[pop_name]]$A==0)]

sss <- sss*sum(sims[[pop_name]]$Y[sims[[pop_name]]$A==0])/sum(sss)


SA_rebal_ratios <- names(df_to_g_A1) %>% lapply(function(pop_name){
  
premA_bycomp <- rep(0, n)
premA_bycomp[which(sims[[pop_name]]$A==1)] <-  scores_A1[[pop_name]]$SA(x = sims[[pop_name]]$X, d=sims[[pop_name]]$D)[which(sims[[pop_name]]$A==1)]
premA_bycomp[which(sims[[pop_name]]$A==0)] <-  scores_A0[[pop_name]]$SA(x = sims[[pop_name]]$X, d=sims[[pop_name]]$D)[which(sims[[pop_name]]$A==0)]

premA <-  scores[[pop_name]]$SA(x = sims[[pop_name]]$X, d=sims[[pop_name]]$D)

premApp_bycomp <- rep(0, n)
premApp_bycomp[which(sims[[pop_name]]$A==1)] <-  scores_A1[[pop_name]]$SA.pp(x = sims[[pop_name]]$X, d=sims[[pop_name]]$D)[which(sims[[pop_name]]$A==1)]
premApp_bycomp[which(sims[[pop_name]]$A==0)] <-  scores_A0[[pop_name]]$SA.pp(x = sims[[pop_name]]$X, d=sims[[pop_name]]$D)[which(sims[[pop_name]]$A==0)]

ratios <- c(sum(sims[[pop_name]]$Y)/sum(premA), sum(sims[[pop_name]]$Y[sims[[pop_name]]$A==0])/sum(premA_bycomp[sims[[pop_name]]$A==0]),
  sum(sims[[pop_name]]$Y[sims[[pop_name]]$A==1])/sum(premA_bycomp[sims[[pop_name]]$A==1]),
  sum(sims[[pop_name]]$Y[sims[[pop_name]]$A==0])/sum(premApp_bycomp[sims[[pop_name]]$A==0]),
    sum(sims[[pop_name]]$Y[sims[[pop_name]]$A==1])/sum(premApp_bycomp[sims[[pop_name]]$A==1]))

names(ratios) <- c("market", "A0", "A1", "App0", "App1")

premA_rebal <- premA*ratios[1]
  
premA_bycomp_rebal <- rep(0, n)
premA_bycomp_rebal[which(sims[[pop_name]]$A==1)] <- premA_bycomp[sims[[pop_name]]$A==1]*ratios[3]
premA_bycomp_rebal[which(sims[[pop_name]]$A==0)] <- premA_bycomp[sims[[pop_name]]$A==0]*ratios[2]


premApp_bycomp_rebal <- rep(0, n)
premApp_bycomp_rebal[which(sims[[pop_name]]$A==1)] <- premApp_bycomp[sims[[pop_name]]$A==1]*ratios[5]
premApp_bycomp_rebal[which(sims[[pop_name]]$A==0)] <- premApp_bycomp[sims[[pop_name]]$A==0]*ratios[4]


## on test data to reduce size of graph here
test_premA_bycomp <- rep(0, n/10)
test_premA_bycomp[which(test[[pop_name]]$A==1)] <-  scores_A1[[pop_name]]$SA(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==1)]
test_premA_bycomp[which(test[[pop_name]]$A==0)] <-  scores_A0[[pop_name]]$SA(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==0)]

test_premApp_bycomp <- rep(0, n/10)
test_premApp_bycomp[which(test[[pop_name]]$A==1)] <-  scores_A1[[pop_name]]$SA.pp(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==1)]
test_premApp_bycomp[which(test[[pop_name]]$A==0)] <-  scores_A0[[pop_name]]$SA.pp(x = test[[pop_name]]$X, d=test[[pop_name]]$D)[which(test[[pop_name]]$A==0)]

test_premA_bycomp_rebal <- rep(0, n/10)
test_premA_bycomp_rebal[which(test[[pop_name]]$A==1)] <- test_premA_bycomp[test[[pop_name]]$A==1]*ratios[3]
test_premA_bycomp_rebal[which(test[[pop_name]]$A==0)] <- test_premA_bycomp[test[[pop_name]]$A==0]*ratios[2]


test_premApp_bycomp_rebal <- rep(0, n/10)
test_premApp_bycomp_rebal[which(test[[pop_name]]$A==1)] <- test_premApp_bycomp[test[[pop_name]]$A==1]*ratios[5]
test_premApp_bycomp_rebal[which(test[[pop_name]]$A==0)] <- test_premApp_bycomp[test[[pop_name]]$A==0]*ratios[4]

##
list(ratios=ratios, premApp_bycomp_rebal=premApp_bycomp_rebal, premA_bycomp_rebal=premA_bycomp_rebal, premA_rebal=premA_rebal,
     test_premApp_bycomp_rebal=test_premApp_bycomp_rebal,
     test_premA_bycomp_rebal=test_premA_bycomp_rebal)
})
names(SA_rebal_ratios) <- names(sims)

lapply(names(sims), function(i) SA_rebal_ratios[[i]]$ratios)

```


With the pp versions, we seem to have problems with scenarios 1 to 3. We see in the following graph that we find again a similar pattern as with the "Portfolio-specific" version of the Aware score, after we rebalance.

```{r}
(to_save_Awarepoprebal_vsX <- names(df_to_g_A1)[1:3] %>% lapply(function(pop_name){
  
  temp <- df_to_g[[pop_name]][,c(1,2,5)]
  temp$SA <- temp$SA*SA_rebal_ratios[[pop_name]]$ratios["market"]
  
  temp_1 <- df_to_g_A1[[pop_name]][,c(1,2,6)]
  temp_1$SA.pp <- temp_1$SA.pp*SA_rebal_ratios[[pop_name]]$ratios["App1"]
  temp_0 <- df_to_g_A0[[pop_name]][,c(1,2,6)]
  temp_0$SA.pp <- temp_0$SA.pp*SA_rebal_ratios[[pop_name]]$ratios["App0"]
  
graph_to_return <- temp %>% rename(SA.pp = SA) %>%
  rbind(temp_1, temp_0)%>% 
  mutate(Portfolio=rep(c("market","A=1","A=0"), each=dim(df_to_g_A0$original)[1])) 


## the colors
    graph_to_return$Portfolio <- factor(graph_to_return$Portfolio,
                                levels = names(colors_for_gg_market))
    
    ## Make sure to keep the right order
    cols <- levels(graph_to_return$Portfolio) %>% sapply(function(lvl){
      colors_for_gg_market[which(lvl == names(colors_for_gg_market))] %>% unname
    })
    
    pop_id <- which(names(df_to_g_A1) == pop_name)
    
    # keep only axis for last plot
    if(which(pop_name == names(df_to_g_A1)) == 1){
      the_y_label <- latex2exp::TeX("Aware premium (market prop + rebalanced)")
      the_x_label <- NULL
    } else if(which(pop_name == names(df_to_g_A1)) == 4){ # If it's on the left, apply correct xlabels
      the_y_label <- latex2exp::TeX("Aware premium (market prop + rebalanced)")
      the_x_label <- latex2exp::TeX("$x$")
    } else if(which(pop_name == names(df_to_g_A1)) %in% c(5, 6)){ # If it's on the left, apply correct xlabels
      the_y_label <- NULL
      the_x_label <- latex2exp::TeX("$x$")
    } else { 
      the_y_label <- NULL
      the_x_label <- NULL
    }

graph_to_return %>%
  filter(x >= -9, x <= 10) %>% 
  ggplot(aes(x=x, y=SA.pp, 
             col=Portfolio,
             fill=Portfolio,
             linetype =Portfolio))+
  geom_line(alpha = 0.75, linewidth = 1) +
  scale_color_manual(values = cols, name = "A") +
  scale_fill_manual(values = cols, name = "A") +
  scale_linetype_manual(values = c(1, 3, 5), name = "A") +
labs(x = the_x_label,
       y = the_y_label,
       title = latex2exp::TeX(long_labels_for_parms[pop_name]))+
    scale_x_continuous(breaks = c(-3:3)*4 )  +
    scale_y_continuous(breaks = seq(70, 150, by=20), limits=c(70,150)) +
    theme_classic()+
  theme(plot.title = element_text(hjust=0.5))
})%>% ggpubr::ggarrange(plotlist = .,
                           nrow = 1, ncol=3,
                           widths = 15, heights = 1,
                           common.legend = T,
                           legend = 'right'))
```


Compare the premiums after rebalancing: Aware versus Aware.pp:

```{r rebal1, fig.width=12, fig.height=8, echo=FALSE}
(to_save_rebal <- names(df_to_g_A1)[1:3] %>% lapply(function(pop_name){
  
  df_to_graph <- data.frame(Aware = SA_rebal_ratios[[pop_name]]$test_premA_bycomp_rebal, 
                            AwarePP = SA_rebal_ratios[[pop_name]]$test_premApp_bycomp_rebal,
                            A = test[[pop_name]]$A)
  
   if(which(pop_name == names(df_to_g_A1)) == 1){
      the_y_label <- latex2exp::TeX("$\\tilde{\\mu}^*_{j,pb}(x)$")
      the_x_label <- NULL
    } else if(which(pop_name == names(df_to_g_A1)) == 4){ # If it's on the left, apply correct xlabels
      the_y_label <- latex2exp::TeX("$\\tilde{\\mu}^*_{j,pb}(x)$")
      the_x_label <- latex2exp::TeX("$\\tilde{\\mu}_{pb}(x|A=j)$")
    } else if(which(pop_name == names(df_to_g_A1)) %in% c(5, 6)){ # If it's on the left, apply correct xlabels
      the_y_label <- NULL
      the_x_label <- latex2exp::TeX("$\\tilde{\\mu}_{pb}(x|A=j)$")
    } else { 
      the_y_label <- NULL
      the_x_label <- NULL
    }
  
  ggplot(df_to_graph, aes(x=Aware, y=AwarePP, col=factor(A), shape=factor(A)))+
    geom_point(alpha=0.7)+
labs(x = the_x_label,
       y = the_y_label,
       title = latex2exp::TeX(long_labels_for_parms[pop_name]))+
    theme_classic()+
  theme(plot.title = element_text(hjust=0.5))+
   scale_color_manual(values=colors_for_gg_A, name="A")+
    scale_shape_manual(values=c(16,17),name="A")+
    geom_abline()
})%>% ggpubr::ggarrange(plotlist = .,
                           nrow = 1, ncol=3,
                           widths = 15, heights = 1,
                           common.legend = T,
                           legend = 'right'))


ggsave(filename = "figs/graph_rebal.pdf",
       plot = to_save_rebal,
       height = 3,
       width = 9,
       units = "in",
       device = "pdf", dpi = 500)
```

A table instead. 

```{r}
corr_table <-  names(df_to_g_A1)[1:3] %>% sapply(function(pop_name){
   
   c('Pearson' =   cor(SA_rebal_ratios[[pop_name]]$test_premA_bycomp_rebal,
       SA_rebal_ratios[[pop_name]]$test_premApp_bycomp_rebal, method = 'pearson'),
     'Kendall' = cor(SA_rebal_ratios[[pop_name]]$test_premA_bycomp_rebal,
       SA_rebal_ratios[[pop_name]]$test_premApp_bycomp_rebal, method = 'kendall'),
     'Spearman' = cor(SA_rebal_ratios[[pop_name]]$test_premA_bycomp_rebal,
       SA_rebal_ratios[[pop_name]]$test_premApp_bycomp_rebal, method = 'spearman'))

})

xtable::xtable(corr_table, digits = 4)
```




